---
title: "beta-stats"
author: "Theresa Cheng"
date: "October 17, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, echo=FALSE}
#knitr::opts_chunk$set(echo = TRUE)

## Load required packages ##
packages <-  c("lme4", "nlme", "zoo", "plyr", "dplyr", "tidyr", "ggplot2", "knitr", "parallel", "data.table", "lubridate","psych")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

# set scientific notation off unless >6 digits
options(scipen=6) 

rm(list=ls())

regmodels = readRDS("/Volumes/TDS/bids_data/derivatives/Cheng_SAP/regmodels.RDS")
```

```{r id coi target networks, include=TRUE}

## identify COI seed
regmodels$seed=gsub('(^\\w{4,9}_\\d{2,3})_.*','\\1',regmodels$coi)

## identify COI target
regmodels$ParcelID= 
  ifelse(startsWith((gsub('aseg_\\d\\d_(.*)','\\1',regmodels$coi)), "aseg"), # if it starts with aseg
       gsub('aseg_\\d\\d_(aseg_\\d\\d)','\\1',regmodels$coi), # then call coitarget aseg_##
       gsub('aseg_\\d\\d_\\wh.Parcel_(.*)','\\1',regmodels$coi)) # but if not, coitarget is the Gordon parcel number

## Load Gordon parcel data
parcels=read.csv("/projects/dsnlab/tds/TDS_scripts/rsfMRI/Cheng_SAP/Parcels/Parcels.csv")
parcels$ParcelID=as.character(parcels$ParcelID)

## Match COI target with Gordon parcel #
regmodels=merge(regmodels, parcels, by="ParcelID", all.x=TRUE)

# turn NA community values into "None"/factor #7
regmodels$Community= ifelse(is.na(regmodels$Community), 7, regmodels$Community)
sum(is.na(regmodels$Community))
regmodels$Community= as.factor(mapvalues(regmodels$Community, c(1:13), c("Auditory", "CinguloOperc", "CinguloParietal", "Default", "DorsalAttn", "FrontoParietal", "None", "RetrosplenialTemporal", "Salience", "SMhand", "SMmouth", "VentralAttn", "Visual")))

unfactorize<-c("AIC","BIC","logLik","intercept", "pval_intercept", "n_beta","pval_n","a_beta","pval_a","aXn_beta","pval_aXn")

regmodels=as.data.frame(regmodels)
regmodels[,unfactorize]= as.numeric(as.character(unlist(regmodels[,unfactorize])))

```

## Are both abuse and neglect associated with altered brain connectivity?
To establish that the network is indeed altered, you would probably want to test these numbers against chance (I can help with how if needed).

```{r prop network change with abuse and neglect}

regmodels_NandA= regmodels %>% filter(mod_type=="neglect_abuse") %>% mutate(sig_n=ifelse(pval_n<.05, 1, 0), sig_a=ifelse(pval_a<.05, 1, 0), sig_both=ifelse((sig_n==1 & sig_a==1), 1, 0)) # for the neglect & abuse models, establish a matrix of 1s and 0s indicating whether the beta terms for neglect, abuse, and both are significant

tbl_community= regmodels %>% group_by(Community, seed) %>% summarise(mod_type= n())
tbl_community$mod_type=round(tbl_community$mod_type/5,2) # acquire the Community totals -- this value is divided by 5 because the community count by 5 models per seed

summary_NandA = regmodels_NandA %>% group_by(Community,seed) %>% summarize(sum_sig_n=sum(sig_n), sum_sig_a=sum(sig_a), sum_sig_both=sum(sig_both)) # count the # of significant N, A, and boths

# now divide by the totals to acquire percentages
summary_NandA$comm_total=tbl_community$mod_type
summary_NandA$pct_n= round(summary_NandA$sum_sig_n/summary_NandA$comm_total, 2)
summary_NandA$pct_a= round(summary_NandA$sum_sig_a/summary_NandA$comm_total, 2)
summary_NandA$pct_both= round(summary_NandA$sum_sig_both/summary_NandA$comm_total, 2)

summary_NandA= summary_NandA %>% gather(pct_n, pct_a, pct_both, key="model_prop", value="percent")
summary_NandA$model_prop <- factor(summary_NandA$model_prop)

kable(summary_NandA, format="pandoc", caption= "proportion of connections driven \n by neglect, abuse, or both (by community)")
```

### Plot

```{r plot, echo=FALSE}
         
ggplot(summary_NandA, aes(x=Community, y=percent, fill=model_prop)) +
  geom_bar(position="dodge", stat="identity") +
  scale_x_discrete(labels=c("A", "CO","CP","D", "DA","FP","NA","RT","S","h","m","VA","V")) +
  ggtitle("%age of sig beta values across seeds")

ggplot(summary_NandA, aes(x=Community, y= percent, fill=Community)) +
  geom_bar(position="dodge", stat="identity") +
  scale_x_discrete(labels=c("A", "CO","CP","D", "DA","FP","NA","RT","S","h","m","VA","V")) +
  facet_grid(seed ~ model_prop) +
  ggtitle("%age of sig beta values across parameters & seeds")
```

## 1.a. Are all connections affected equally or are they affected differentially for different networks?

Count the significant connections, or % connections, within each network separately, for A and N separately. You could use chi-square test to test for significance of differences between networks or between N & A. (Perhaps significance tests not necessary for the first pass, simple descriptives may be already telling).

TC: I think this analysis was run above, unless by A and N separately you mean in the separate neglect and abuse models. To do next: Run chi-square test. 

You could use this data to evaluate whether previously reported effects of abuse are consistent with this analysis once you control for neglect etc.

TC note to self: pull up and compare with existing literature.

# 2. Do the effects of abuse and neglect interact?

For this question, you would use the full model and determine the number of connections that have a significant interaction term.

You can look at what specific pattern that interaction has for each connection (or each family of connections - although I’m not sure if averaging across connections would be appropriate for this analysis).

```{r}
regmodels_NXA= regmodels %>% filter(mod_type=="neglect_abuse_int") %>% mutate(sig_aXn=ifelse(pval_aXn<.05, 1, 0))

tbl_community= regmodels_NXA %>% group_by(Community, seed) %>% summarise(mod_type= n())

summary_NXA = regmodels_NXA %>% group_by(Community,seed) %>% summarize(sum_sig_aXn=sum(sig_aXn))
summary_NXA$comm_total=tbl_community$mod_type
summary_NXA$pct_aXn= round(summary_NXA$sum_sig_aXn/summary_NXA$comm_total, 2)

kable(summary_NXA, format="pandoc", caption= "proportion of connections driven \n by neglect X abuse interactions (by community)")
```

```{r plot interactions}
ggplot(summary_NXA, aes(x=Community, y=pct_aXn, fill=Community)) +
  geom_bar(position="dodge", stat="identity") +
  scale_x_discrete(labels=c("A", "CO","CP","D", "DA","FP","NA","RT","S","h","m","VA","V")) +
  ggtitle("%age of sig beta values across seeds")

ggplot(summary_NXA, aes(x=Community, y= pct_aXn, fill=Community)) +
  geom_bar(position="dodge", stat="identity") +
  scale_x_discrete(labels=c("A", "CO","CP","D", "DA","FP","NA","RT","S","h","m","VA","V")) +
  facet_grid(seed~.) +
  ggtitle("%age of sig beta values across parameters & seeds")

# next: need to plot directionality in more detail

```


