---
title: 'TDS Dimensions of Adversity: Descriptive Stats'
author: "Theresa Cheng"
date: "April 13, 2017"
output:
html_document: default
pdf_document: default
---

# NOTE: Edited on 10/19 to subset to the Cheng_SAP N=102 sample

#### Evaluate the distribution of responses to questionnaire items pertaining to abuse, neglect, household dysfunction, and economic deprivation in the community, child welfare, and juvenile justice samples of TDS

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())

povline_impute=TRUE # if this is set to 1 (true), household size will be imputed with the mean for each group, rounded down (4 for the community sample and 5 for the dhs and jj samples), affecting the income:needs ratio calculation; otherwise set to 0

```

```{r install packages, include=FALSE}
if(!require(reshape)){install.packages('reshape')} ; library(reshape)
if(!require(plyr)){install.packages('plyr')} ; library(plyr)
if(!require(dplyr)){install.packages('dplyr')} ; library(dplyr)
if(!require(tidyr)){install.packages('tidyr')} ; library(tidyr)
if(!require(knitr)){install.packages('knitr')} ; library(knitr)
if(!require(ggplot2)){install.packages('ggplot2')} ; library(ggplot2)
if(!require(VennDiagram)){install.packages('VennDiagram')} ; library(VennDiagram)
if(!require(GGally)){install.packages('GGally')} ; library(GGally)
```

```{r load ACES data, include=FALSE}

setwd("/Users/theresacheng/Documents/tds_rsfc/Qualtrics") # change path to wherever qualtrics data is

## TDS1: This data is stored in pre- and post- files, relative to IRB approval of additional questionnaires
df1= rbind.fill(read.csv("TDS-1-PRE-auto_scored_scales_wide.csv", header=TRUE),  read.csv("TDS-1-POST-auto_scored_scales_wide.csv", header=TRUE)) # load pre/post, remove blank rows, and merge
df1=cbind(SID=df1$SID, select(df1,starts_with("ACE_ace_abuse")), select(df1,starts_with("ACE_ace_neglect")), select(df1,starts_with("ACE_ace_hh")), select(df1,starts_with("ACE_ace_hh"))) # subset relevant items: abuse, neglect, hh

## TDS2
df2= read.csv("TDS-2-auto_scored_scales_wide.csv", header=TRUE) # load data
df2=cbind(SID=df2$SID, select(df2,starts_with("ACE_ace_abuse")),  select(df2,starts_with("ACE_ace_neglect")), select(df2,starts_with("ACE_ace_hh")), select(df2,starts_with("ACE_ace_hh"))) # subset relevant items: abuse, neglect, hh

## Data cleaning
df_aces= rbind.fill(df1, df2) %>% filter(is.na(.$SID)==FALSE) # merge TDS1 and TDS2, remove NA rows

fn <- substr(df_aces$SID,1,1)
df_aces$group= ifelse(fn %in% "1", "comm", 
               ifelse(fn %in% "3", "dhs",
               "jj"))
```

```{r acquire age and sex}

setwd("/Volumes/TDS/behavior/Redcap")
df_demo=read.csv("age_gender_iq.csv")
```

```{r subset participants}

subset=TRUE

if (subset==TRUE) {
  # Subset to Cheng_SAP participants, N=102
  load("/Volumes/TDS/bids_data/derivatives/Cheng_SAP/gordon_coisDT.RDS") 
  subjectList= as.data.frame(unique(gordon_coisDT$sub))
  subjectList=(separate(subjectList, col=1, into=c("junk", "sub"), sep="-"))[,-1]
  
  df_aces$SID= as.character(df_aces$SID) 
  df_aces= df_aces %>% filter(SID %in% subjectList) # filter df_aces by those who have gordon_cois
  df_demo= df_demo %>% filter(subject.name %in% subjectList)
}
```

```{r load ses data}
setwd("/Users/theresacheng/Documents/tds_rsfc/Qualtrics") # need to change path to wherever qualtrics data is

# Economic Deprivation 
#### Notes: PAL2_5 a score of 4= Not enough to get by; PAL2_7 is # of people in household

## TDS1: This data is stored within pre- and post- files, relative to IRB approval of additional questionnaires
df1_raw= rbind.fill( read.csv("TDS-1-PRE-auto_raw_qualtrics_long.csv", header=TRUE), read.csv("TDS-1-POST-auto_raw_qualtrics_long.csv", header=TRUE)) 
df1_ed= rbind.fill(filter(df1_raw, item=="Income"), filter(df1_raw, item=="PAL2_5"), filter(df1_raw, item=="PAL2_7")) %>% select(SID, item, value) %>% 
spread(key=item, value=value) 

## TDS2
df2_raw= read.csv("TDS-2-auto_raw_qualtrics_long.csv", header=TRUE) 
df2_ed= rbind.fill(filter(df2_raw, item=="Income"), filter(df2_raw, item=="PAL2_5"), filter(df2_raw, item=="PAL2_7")) %>% select(SID, item, value) %>% spread(key=item, value=value) 

## Data Cleaning
df_ed=rbind.fill(df1_ed, df2_ed) # add group label: dhs, jj, comm

fn <- substr(df_ed$SID,1,1) # generate string of first number of SIDs
df_ed$group= ifelse(fn %in% "1", "comm", 
            ifelse(fn %in% "3", "dhs",
               "jj")) # match strings to group labels

# calculate average household size per group
mean_hh= ddply(df_ed, .(group), summarize, mean(PAL2_7, na.rm=TRUE))
mean_hh
                                    
# generate income to needs and poverty line variables
income_lowerbound= as.numeric(ifelse(df_ed$Income %in% "1", "9999", 
             ifelse(df_ed$Income %in% "2", "10000",
             ifelse(df_ed$Income %in% "3", "15000",
             ifelse(df_ed$Income %in% "4", "20000",
             ifelse(df_ed$Income %in% "5", "25000",
             ifelse(df_ed$Income %in% "6", "30000",
             ifelse(df_ed$Income %in% "7", "35000",
             ifelse(df_ed$Income %in% "8", "40000",
             ifelse(df_ed$Income %in% "9", "50000",
             ifelse(df_ed$Income %in% "10", "60000",
             ifelse(df_ed$Income %in% "11", "80000",
             ifelse(df_ed$Income %in% "12", "100000",
             ifelse(df_ed$Income %in% "13", "150000", "NA"))))))))))))))

if (povline_impute==1) {
fedpovlev_byh = as.numeric(ifelse(df_ed$PAL2_7 %in% "1", "12060", # from 2017 guidelines
             ifelse(df_ed$PAL2_7 %in% "2", "16240",
             ifelse(df_ed$PAL2_7 %in% "3", "20420",
             ifelse(df_ed$PAL2_7 %in% "4", "24600",
             ifelse(df_ed$PAL2_7 %in% "5", "28780",
             ifelse(df_ed$PAL2_7 %in% "6", "32960",
             ifelse(df_ed$PAL2_7 %in% "7", "37140",
             ifelse(df_ed$PAL2_7 %in% "8", "41320",
             ifelse(df_ed$PAL2_7 %in% "9", "45500",
             ifelse(df_ed$PAL2_7 %in% "10", "49680",
             ifelse(df_ed$PAL2_7 %in% "11", "53860",
             ifelse(df_ed$PAL2_7 %in% "12", "58040", 
             ifelse(df_ed$group=="comm", "24600", # avg for hh_size=4
             ifelse(df_ed$group=="dhs" | df_ed$group=="jj", "28780", #avg for hh_size=5
                    "NA")))))))))))))))
} else {
  fedpovlev_byh = as.numeric(ifelse(df_ed$PAL2_7 %in% "1", "11880", 
             ifelse(df_ed$PAL2_7 %in% "2", "16020",
             ifelse(df_ed$PAL2_7 %in% "3", "20160",
             ifelse(df_ed$PAL2_7 %in% "4", "24300",
             ifelse(df_ed$PAL2_7 %in% "5", "28440",
             ifelse(df_ed$PAL2_7 %in% "6", "32580",
             ifelse(df_ed$PAL2_7 %in% "7", "36730",
             ifelse(df_ed$PAL2_7 %in% "8", "40890",
             ifelse(df_ed$PAL2_7 %in% "9", "40890",
             ifelse(df_ed$PAL2_7 %in% "10", "45050",
             ifelse(df_ed$PAL2_7 %in% "11", "49210",
             ifelse(df_ed$PAL2_7 %in% "12", "53370", "NA")))))))))))))}

df_ed$income_to_needs= income_lowerbound/fedpovlev_byh 
df_ed$log_income_to_needs=log(df_ed$income_to_needs)
df_ed$povline= as.integer(ifelse(df_ed$Income %in% c("1", "2"), "1", 
                      ifelse(df_ed$income_to_needs<1, "1", 0))) # If the value for income is 1 or 2, assuming that kids' household size 2+, then they are below the poverty line. So even w/o household size data, they will get a 1. Otherwise, calculate whether the income to needs ratio is indeed <1. 

# keep ACE scores only if less than or equal to 1 item is missing per subscale, otherwise replace with NA; Convert to factors

df_aces$ACE_abuse_num= ifelse(df_aces$ACE_ace_abuse_n_missing<=1, mapvalues(df_aces$ACE_ace_abuse_score, from=c("0","0.333333333333333", "0.666666666666667","1"), to=c("0", "1","2","3")), "NA")
df_aces$ACE_abuse_num= as.factor(df_aces$ACE_abuse_num)

df_aces$ACE_neglect_num= ifelse(df_aces$ACE_ace_neglect_n_missing<=1, mapvalues(df_aces$ACE_ace_neglect_score, from=c("0","0.5","1"), to=c("0", "1","2")), "NA")
df_aces$ACE_neglect_num=as.factor(df_aces$ACE_neglect_num)

df_aces$ACE_hh_dysf_num= ifelse(df_aces$ACE_ace_hh_dysf_n_missing<=1, mapvalues(df_aces$ACE_ace_hh_dysf_score, from=c("0","0.25", "0.333333333333333", "0.5", "0.666666666666667", "0.75", "1"), to=c("0", "1","1", "2","2","3","4")), "NA")
df_aces$ACE_hh_dysf_num= as.factor(df_aces$ACE_hh_dysf_num)

df_aces=filter(df_aces, !is.na(ACE_abuse_num))

```

## How much missing data is there?
```{r missing data, echo=FALSE}

## ACES
df_aces_mi = df_aces %>% 
  group_by(group) %>% 
  summarise(abuse_mi = sum(ACE_ace_abuse_n_missing, na.rm=TRUE), 
                      neglect_mi = sum(ACE_ace_neglect_n_missing, na.rm=TRUE), 
                      hh_mi = sum(ACE_ace_hh_dysf_n_missing, na.rm=TRUE))
kable(df_aces_mi, caption="ACES") 

## Economic deprivation
df_ed_mi = df_ed %>% group_by(group) %>% summarise(income_mi=sum(is.na(Income)), enough_mi=sum(is.na(PAL2_5)), hhsize_mi=sum(is.na(PAL2_7)),povline_mi=sum(is.na(povline)))
kable(df_ed_mi, caption="Economic Deprivation")
```

## How many subjects are in each group?
```{r total per group, echo=FALSE}

# Merge dataframes 
df_ed$SID=as.character(df_ed$SID)
df_aces$SID=as.character(df_aces$SID)
df=left_join(df_aces, df_ed, by=c("SID","group"))
#rm(list=setdiff(ls(), c("df", "df_demo")))

# rename PAL2_5 to "enough"as in, did participants have enough to get by
df = df %>% dplyr::rename("enough"=PAL2_5, "hhsize"=PAL2_7)

# make group a factor
df$group=as.factor(df$group)

tbl=ddply(df, .(group), summarize, count=NROW(SID))
kable(tbl, format="pandoc")

```

## What are the basic descriptive stats and distributions for our variables of interest? [Economic Deprivation]
```{r Distributions_EconDep, warning=FALSE}

tbl=ddply(df, .(group), summarize, count=sum(!is.na(income_to_needs)))
kable(tbl, format="pandoc", caption="Income:Needs Data; N by group")

# What is the distribution of the income to needs ratio by group?
ggplot(df, aes(x=income_to_needs, fill=group)) + 
   geom_density(alpha=.3) + 
  ggtitle(paste("Distribution of income to needs ratio by group (N=", sum(!is.na(df$income_to_needs)), ")", sep=""))

# What is the distribution of the log-transformed values of income to needs ratio by group?
ggplot(df, aes(x=log_income_to_needs, fill=group)) + 
  geom_density(alpha=.3) + 
  ggtitle(paste("Distribution of log-transformed income to needs ratio by group (N=", sum(!is.na(df$log_income_to_needs)), ")", sep=""))

# What is the mean and sd for income:needs and log(income:needs) ratio by group?
tbl=ddply(df, .(group), summarize, mean_ItN=mean(income_to_needs, na.rm=TRUE), sd_ItN=sd(income_to_needs, na.rm=TRUE), mean_logItN=mean(log_income_to_needs, na.rm=TRUE), sd_logItN=sd(log_income_to_needs, na.rm=TRUE))
kable(tbl)

# How many individuals from each group live below the poverty line?
# ggplot(data=filter(df, df$povline=="1"), aes(x=povline, fill=group)) + 
#    geom_histogram(position="dodge", bins=1) + 
#   ggtitle(paste("Proportion of subjects living below the poverty line (N=", sum(!is.na(df$povline)), ")", sep=""))
```

## What are the distributions of variables of interest? [ACES]
```{r Distributions_ACES, warning=FALSE}

# What is the distribution of the ACE child abuse score by group?
ggplot(df, aes(x=ACE_abuse_num, fill=group)) + 
  geom_bar(position="dodge") + 
  ggtitle(paste("Number of ACE abuse items endorsed by group (N=", sum(!is.na(df$ACE_ace_abuse_score)), ")", sep=""))

# What is the distribution of the ACE neglect score by group?
ggplot(df, aes(x=ACE_neglect_num, fill=group)) + 
  geom_bar(position="dodge") + 
  ggtitle(paste("Number of ACE neglect items endorsed by group (N=", sum(!is.na(df$ACE_ace_neglect_score)), ")", sep=""))

# What is the distribution of the ACE household dysfunction score by group?
ggplot(df, aes(x=ACE_hh_dysf_num, fill=group)) + 
  geom_bar(position="dodge") + 
  ggtitle(paste("Number of ACE household dysfunction items endorsed by group (N=", sum(!is.na(df$ACE_ace_hh_dysf_score)), ")", sep=""))

# What is the mean and sd for income:needs and log(income:needs) ratio by group?
tbl=ddply(df, .(group), summarize, mean_abuse=mean(ACE_ace_abuse_score, na.rm=TRUE), sd_abuse=sd(ACE_ace_abuse_score, na.rm=TRUE), mean_neglect=mean(ACE_ace_neglect_score, na.rm=TRUE), sd_neglect=sd(ACE_ace_neglect_score, na.rm=TRUE), mean_hh_dysf=mean(ACE_ace_hh_dysf_score, na.rm=TRUE), sd_hh_dysf=sd(ACE_ace_hh_dysf_score, na.rm=TRUE))
kable(tbl)
```

# Continuous Data
```{r correlations, warning=FALSE}
df_pairs=cbind.data.frame(df$ACE_ace_abuse_score, df$ACE_ace_neglect_score,  df$group)
colnames(df_pairs)=c("abuse","neglect", "group") #df$ACE_ace_hh_dysf_score, df$income_to_needs, "H","ItN",

ggpairs(df_pairs)
```

# Categorical Data
##What is the overlap of ACE scores across groups?
#### For these, each participant with a score of at least 1 in each category
```{r venn diagrams, warning=FALSE}

area1 = nrow(subset(df, ACE_ace_abuse_score>=.1))
area2 = nrow(subset(df, ACE_ace_neglect_score>=.1))
area3 = nrow(subset(df, ACE_ace_hh_dysf_score>=.1))
n12=nrow(subset(df, ACE_ace_abuse_score>=.1 & ACE_ace_neglect_score>=.1))
n23= nrow(subset(df, ACE_ace_neglect_score>=.1 & ACE_ace_hh_dysf_score>=.1))
n13 = nrow(subset(df, ACE_ace_abuse_score>=.1 & ACE_ace_hh_dysf_score>=.1))
n123=nrow(subset(df, ACE_ace_abuse_score>=.1 & ACE_ace_neglect_score>=.1 & ACE_ace_hh_dysf_score>=.1))

# Abuse and neglect
grid.newpage()
draw.pairwise.venn(area1, area2, n12, category = c("Abuse", "Neglect"), lty = "blank", 
    fill = c("skyblue", "pink1"), scaled=TRUE)

# Abuse, neglect, and household dysfunction
grid.newpage()
draw.triple.venn(area1, area2, area3, n12, n23, n13, n123, category = c("Abuse", "Neglect", "Household Dysfunciton"), lty = "blank", 
    fill = c("skyblue", "pink1", "mediumorchid"))
```

## Let's examine the breakdown of ACE and economic deprivation scores between groups
```{r}

df_binary=as.data.frame(cbind(SID=df$SID, 
                              group=df$group, 
                              ACE_abuse_binary=(df$ACE_ace_abuse_score>=.1),
                              ACE_neglect_binary=(df$ACE_ace_neglect_score>=.1),
                              ACE_hh_dysf_binary=(df$ACE_ace_hh_dysf_score>=.1), 
                              povline=(df$povline)))

df_binary$SID=as.character(df_binary$SID)
colnames(df_binary)=c("SID", "group", "A", "N", "H", "P")
df_binary$group=factor(df_binary$group, levels=c("1","2"), labels=c("comm","dhs"))
df_binary$A=factor(df_binary$A, levels=c("FALSE","TRUE"), labels=c("","A"))
df_binary$N=factor(df_binary$N, levels=c("FALSE","TRUE"), labels=c("","N"))

# What is the distribution of the ACE abuse X neglect scores by group?
ggplot(df_binary, aes(x=interaction(N, A), fill=interaction(N, A))) + 
  geom_bar(position="dodge") + 
  guides(fill=FALSE) +
  scale_fill_discrete(name="",labels=c("None", "N", "A","N&A")) +
  scale_x_discrete(labels=c("None", "N", "A","N&A")) + 
  labs(x="categories")
  #ggtitle(paste0("ACES items endorsed by group (N=", nrow(df), ")"))

ggplot(df_binary, aes(x=interaction(A,N,H,P), fill=interaction(A,N,H,P))) + 
  geom_bar() + 
  theme(axis.text.x= element_text(size=rel(.7))) + 
  scale_fill_discrete(name="", labels=c("None", "A","N","AN", "H","AH","NH","ANH", "P","NP","ANP","HP","AHP","NHP","ANHP")) + 
  scale_x_discrete(labels=c("None", "A","N","AN", "H","AH","NH","ANH", "P","NP","ANP","HP","AHP","NHP","ANHP")) +
  ggtitle("Abuse, neglect, household dysfunction, and poverty")

ggplot(df_binary, aes(x=interaction(A,N,H,P), fill=interaction(A,N,H,P))) +
  geom_bar() + 
  theme(axis.text.x= element_text(size=rel(.5))) + 
   facet_grid(. ~group) +
  scale_fill_discrete(name="", labels=c("None", "A","N","AN", "H","AH","NH","ANH", "P","NP","ANP","HP","AHP","NHP","ANHP"))+
  scale_x_discrete(labels=c("None", "A","N","AN", "H","AH","NH","ANH", "P","NP","ANP","HP","AHP","NHP","ANHP")) +
    ggtitle("Abuse, neglect, household dysfunction, and poverty by group")

ggplot(df_binary, aes(x=interaction(A,N,P), fill=interaction(A,N,P))) +
  geom_bar() + 
  facet_grid(. ~group)+
  theme(axis.text.x= element_text(size=rel(.5))) +
  scale_fill_discrete(name="", labels=c("None", "A","N","AN","P","NP","ANP")) +
  scale_x_discrete(labels=c("None", "A","N","AN","P","NP","ANP")) +
  ggtitle("Abuse, neglect, and poverty by group")

# Acquire summary statistics of demographics by exposure status
colnames(df_demo)[1]="SID"
df_demo$SID=as.character(df_demo$SID)
df_binary_summary= inner_join(x=df_binary, y=df_demo) %>% inner_join(df_ed) %>% group_by(A,N) %>% summarize(mean_age=mean(age), sem_age=sd(age)/sqrt(length(df_binary)), count_sex=sum(gender), mean_iq=mean(iq), sem_iq=sd(iq)/sqrt(length(df_binary)), mean_ItN=mean(income_to_needs, na.rm=TRUE), sem_ItN=sd(income_to_needs, na.rm=TRUE)/sqrt(length(df_binary)))

df_binary$group=factor(df_binary$group, labels=c("Community Sample", "CWS Sample"))

ggplot(df_binary, aes(x=interaction(A,N), fill=interaction(A,N))) +
  geom_bar(position="dodge") +
  facet_grid(.~group) +
  scale_x_discrete(labels=c("None", "Abuse","Neglect","Both")) +
  xlab("Exposures") +
  ylab("Count") +
  theme(legend.position="none")

#ggplot(df_binary, aes(x=interaction(A,N,H,P), y=interaction(A,N,H,P))) + 
 # geom_tile(aes(fill=interaction(A,N,H,P)))

```

## What are the basic descriptive stats and distributions for demographic variables?
```{r descriptive stats}

colnames(df_demo)[1] = ("SID")
df=join(df_demo, df, by="SID")

df_pairs=cbind.data.frame(df$ACE_ace_abuse_score, df$ACE_ace_neglect_score,  df$group, df$age, df$gender, df$iq)
colnames(df_pairs)=c("abuse","neglect", "group", "age", "gender", "IQ") #df$ACE_ace_hh_dysf_score, df$income_to_needs, "H","ItN",

ggpairs(df_pairs)

```

# Get subject list
### Acquire a subject list for participants in TDS 1 and TDS 2 (no juvenile justice kiddos) who have data for abuse, neglect, household dysfunction, and economic deprivation

```{r Get Subject List}
df_scores_complete=cbind(df$SID, df_pairs)
colnames(df_scores_complete)[1]="SID"
df_scores_complete=na.omit(df_scores_complete)
df_scores_complete=df_scores_complete[- grep("^4", df_scores_complete$SID),]

df_scores_complete$SID
```
