---
title: "id.events_cyb1"
author: "NV"
date: "May 3, 2017"
output: html_document
---
  
  # Nandita Vijayakumar
  # 5/3/2017
  # This script uses output of "collect_data_for_cyberball.Rmd"
  # This script identifies events within Cyberball run 1 and pmods
  # ct_2P: throws from computer to player
  # ct_2C: throws from computer to computer
  # PT: throws by player
  # PC: participant catches
  # Run this script first without mean centered pmod, then run "Finding grand mean.R" to identify appropriate mean for centering.
  
#########
#!!! Remember to run 'module add R' at the command line first
#########
#Paths are set to run locally, not on the grid.

```{r}
# LOAD PACKAGES
osuRepo<-'http://ftp.osuosl.org/pub/cran/'

#Check if the packages we need are installed, and if not, install them
if(!require(plyr)){
  install.packages('plyr',repos=osuRepo)
}
library(plyr)

if(!require(dplyr)){
  install.packages('dplyr',repos=osuRepo)
}
library(dplyr)
if(!require(tidyr)){
  install.packages('tidyr',repos=osuRepo)
}
library(tidyr)
if(!require(data.table)){
  install.packages('data.table',repos=osuRepo)
}
library(data.table)
if(!require(R.matlab)){
  install.packages('R.matlab',repos=osuRepo)
}

if(!require(chron)){
  install.packages('R.matlab',repos=osuRepo)
}
library(chron)
library(R.matlab)
```

```{r} 
# LOAD FILES
rm(list=ls())

#define folder locations
tds_folder<-'/Volumes/TDS/'
labeled_cyberball_folder<-'behavior/CyberBall/multiconds/Labelled_Data/'
labeled_files_folder<-paste(tds_folder,labeled_cyberball_folder,sep='')
summary_cyberball_folder<-'behavior/CyberBall/multiconds/Summary/'
group_folder<-'tds1_tds2'
summary_files_folder<-paste(tds_folder,summary_cyberball_folder,group_folder,sep='')
setwd(labeled_files_folder)

#list the files 
listFiles<-list.files(labeled_files_folder,recursive=T, pattern='cyb[1|3].*_1.csv$') #Removing TDS3 participants

# READ IN EACH FILE AND CLEAN IT UP

for(j in 1:length(listFiles)) {
  setwd(labeled_files_folder)
  df<-read.csv(listFiles[j]) #read in the file
  timestamp<-as.character(df[1,2]) #change the timestamp into a character
  
  # Reformat Timestamp Into Hour, Minutes, and Seconds.Milliseconds
  df<-separate(df, "timestamp", c("date", "time"), sep=16)
  df<-separate(df, "time", c("time","junk"), sep=8)
  
  df<-separate(df,"milliseconds",c("junk","milliseconds"), sep=1)
  df$time<-paste(df$time, df$milliseconds, sep="")
  
  #Delete unnecessary variables
  df <- df[,-(5:7)]
  
  df$behavior.num<-mapvalues(df$behavior.type, c("catch(player1)", "catch(player3)","throw(player1)","throw(player3)", "connecting(time: 6)", "throw(player1-player2)", "throw(player3-player2)", "throw(player1-player3)","throw(player3-player1)"),c(4,4,3,3,2,1,1,0,0)) 
  
  # Filter out unnecessary information (catches, participant throws) keep connecting time and all throws from player 1 or 3
  df.blockID<-filter(df, behavior.num==1| behavior.num==2|behavior.num==0)
  
  
  op<-options(digits.secs=5)
  df$time<-strptime(df$time,format="%H:%M:%OS")
  options(op)
  
  # Generate variables that reflect the conditions one trial later
  df$behavior.num1 =lead(df$behavior.num)
  
  ##IDENTIFY wait
  for(i in 1:NROW(df)){
    if (df$behavior.num[i]==2) {
      df$wait.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
      df$wait.durations[i]= difftime(df$time[i+1],df$time[i],unit="secs")}
    else {
      df$wait.onsets[i]=NA
      df$wait.durations[i]=NA}
  }
  
  ##IDENTIFY pt: participant throws
  # Loop specifies that if there are fewer than 1 cyberball action following the catch by a subject, specify duration=0
  for(i in 1:NROW(df)){
    if (df$behavior.num[i]==3 & !(is.na(df$behavior.num1[i]))) {
      df$pt.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
      df$pt.durations[i]= difftime(df$time[i+1],df$time[i],unit="secs")}
    else if (df$behavior.num[i]==3 & is.na(df$behavior.num1[i])) {
      df$pt.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
      df$pt.durations[i]=0 }
    else {
      df$pt.onsets[i]=NA
      df$pt.durations[i]=NA}
  }

##IDENTIFY pc: participant catches
# Loop specifies that if there are fewer than 1 cyberball action following the catch by a subject, specify duration=0
for(i in 1:NROW(df)){
  if (df$behavior.num[i]==4 & !(is.na(df$behavior.num1[i]))) {
    df$pc.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
    df$pc.durations[i]= difftime(df$time[i+1],df$time[i],unit="secs")}
  else if (df$behavior.num[i]==4 & is.na(df$behavior.num1[i])) {
    df$pc.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
    df$pc.durations[i]=0 }
  else {
    df$pc.onsets[i]=NA
    df$pc.durations[i]=NA}
}
  
  ##IDENTIFY ct_2P
  # Loop specifies that if there are fewer than 1 cyberball action following the catch by a subject, specify duration=0
  for(i in 1:NROW(df)){
    if (df$behavior.num[i]==1 & !(is.na(df$behavior.num1[i]))) {
      df$ct_2P.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
      df$ct_2P.durations[i]= difftime(df$time[i+1],df$time[i],unit="secs")}
    else if (df$behavior.num[i]==1 & is.na(df$behavior.num1[i])) {
      df$ct_2P.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
      df$ct_2P.durations[i]=0 }
    else {
      df$ct_2P.onsets[i]=NA
      df$ct_2P.durations[i]=NA}
  }
  
  ##IDENTIFY ct_2C
  # Loop specifies that if there are fewer than 1 cyberball action following the catch by a subject, specify duration=0
  for(i in 1:NROW(df)){
    if (df$behavior.num[i]==0 & !(is.na(df$behavior.num1[i]))) {
      df$ct_2C.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
      df$ct_2C.durations[i]= difftime(df$time[i+1],df$time[i],unit="secs")}
    else if (df$behavior.num[i]==0 & is.na(df$behavior.num1[i])) {
      df$ct_2C.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
      df$ct_2C.durations[i]=0 }
    else {
      df$ct_2C.onsets[i]=NA
      df$ct_2C.durations[i]=NA}
  }
  
  ##IDENTIFY pmods
  
  df.blockID$pmod_ct_2P = 0
  df.blockID$pmod_ct_2C = 0
  
    for(i in 1:NROW(df.blockID)){
      if (df.blockID$behavior.num[i]==1) {
        df.blockID$pmod_ct_2P[i]=1+df.blockID$pmod_ct_2P[i-1]
      } else {
    }}

  for(i in 1:NROW(df.blockID)){
    if (df.blockID$behavior.num[i]==0) {
    df.blockID$pmod_ct_2C[i]=1+df.blockID$pmod_ct_2C[i-1]
      } else {
    }}
        
##FILTER to get final events file
df.ct<-subset(df, behavior.num==1| behavior.num==2| behavior.num==0)
df.ct$Y = df.ct$X
df.blockID$Y = df.blockID$X

ct.info<- merge(df.ct, df.blockID, by="Y")
ct.info$userid<-ct.info$userid.x
ct.info<-ct.info[,c(29,10:11,16:19,27:28)]

ct_2P.info<-subset(ct.info,!(is.na(ct.info$ct_2P.onsets)))
ct_2P.info$names<-"ct_2P"
ct_2P.info$onsets<-ct_2P.info$ct_2P.onsets
ct_2P.info$durations<-0
ct_2P.info$pmod<-ct_2P.info$pmod_ct_2P
ct_2P.info<-ct_2P.info[,c(1,10:13)]

ct_2C.info<-subset(ct.info,!(is.na(ct.info$ct_2C.onsets)))
ct_2C.info$names<-"ct_2C"
ct_2C.info$onsets<-ct_2C.info$ct_2C.onsets
ct_2C.info$durations<-0
ct_2C.info$pmod<-NA
ct_2C.info<-ct_2C.info[,c(1,10:13)]

wait.info<-subset(ct.info,!(is.na(ct.info$wait.onsets)))
wait.info$names<-"wait"
wait.info$onsets<-wait.info$wait.onsets
wait.info$durations<-wait.info$wait.durations
wait.info$pmod<-NA
wait.info<-wait.info[,c(1,10:13)]

pt.info<-subset(df, behavior.num==3)
pt.info$names<-"pt"
pt.info$onsets<-pt.info$pt.onsets
pt.info$durations<-0
pt.info$pmod<-NA
pt.info<-pt.info[,c(2,19:22)]

pc.info<-subset(df, behavior.num==4)
pc.info$names<-"pc"
pc.info$onsets<-pc.info$pc.onsets
pc.info$durations<-0
pc.info$pmod<-NA
pc.info<-pc.info[,c(2,19:22)]

row.names(pt.info) <- seq(nrow(pt.info))
row.names(ct_2P.info) <- seq(nrow(ct_2P.info))
row.names(ct_2C.info) <- seq(nrow(ct_2C.info))
row.names(pc.info) <- seq(nrow(pc.info))

file<-rbind(wait.info,pt.info, ct_2C.info, ct_2P.info, pc.info)

file$names<-mapvalues(file$names,c("wait","pt", "ct_2C","ct_2P","pc"), c(1,2,3,4,5))
file$names<-as.numeric(file$names)
file$onsets<-as.numeric(file$onsets)
file$meanC_pmod = file$pmod - 2.763247 #Comment out this line and run script without meanC_pmod first. Use this output with "Finding grand mean.R" script to identify appropriate value for centering. Then re-run this script with correct mean value.

setwd(summary_files_folder)
write.csv(file,paste("summary_events",listFiles[j], sep="_")) 
}