---
title: "Concatenate Run1 and Run2 Blocks"
author: "NV"
date: "August 30, 2016"
output: html_document
---

```{r}
# LOAD PACKAGES
osuRepo<-'http://ftp.osuosl.org/pub/cran/'

#Check if the packages we need are installed, and if not, install them
if(!require(plyr)){
  install.packages('plyr',repos=osuRepo)
}
library(plyr)

if(!require(dplyr)){
  install.packages('dplyr',repos=osuRepo)
}
library(dplyr)
if(!require(tidyr)){
  install.packages('tidyr',repos=osuRepo)
}
library(tidyr)
if(!require(data.table)){
  install.packages('data.table',repos=osuRepo)
}
library(data.table)
if(!require(R.matlab)){
  install.packages('R.matlab',repos=osuRepo)
}

if(!require(chron)){
  install.packages('R.matlab',repos=osuRepo)
}
library(chron)
library(R.matlab)

require(stringr)
```

```{r, echo=FALSE}
# LOAD FILES
rm(list=ls())

#define folder locations
tds_folder<-'/Volumes/research/tds/'
labeled_cyberball_folder<-'fMRI/analysis/fx/multicond/cyberball/TDS2_labeled_cyb_data'
labeled_files_folder<-paste(tds_folder,labeled_cyberball_folder,sep='')
summary_cyberball_folder<-'fMRI/analysis/fx/multicond/cyberball/TDS2_cyb_summary/blocks/excFpHi'
summary_cyberball_folder_concat<-'fMRI/analysis/fx/multicond/cyberball/TDS2_cyb_summary/blocks/excFpHi_concat'
summary_files_folder<-paste(tds_folder,summary_cyberball_folder,sep='')
summary_files_folder_concat <- paste(tds_folder,summary_cyberball_folder_concat,sep='')
```

```{r}
#Import subject IDs and create list of IDs
setwd('/Volumes/research/tds/behavioral/raw/cyberball')
subjList <- read.csv("SubjectList_full.csv", header = FALSE)
subjList <- subjList$V1

#Within each subject...

for(i in 1:length(subjList)) 
{#Calculate length of first run
 subjID = paste("t",subjList[i],sep = "")
 imageFiles <- paste(tds_folder,"fMRI/subjects/",pattern=toString(subjID),"/ppc/cyb1",sep="")
 setwd(imageFiles)
 listImages <- list.files(imageFiles,pattern='^cyb1_*')
 lastImage <- tail(listImages, n=1)
 lastNum <- as.numeric(substring(lastImage, 6, 9))
 lengthRun1 <- 2*(lastNum)
                          
 #Import summary files for each subject (based on block models)
 setwd(summary_files_folder)
 listFiles <- list.files(summary_files_folder,recursive=T, pattern=toString(subjList[i]))
 inc<-read.csv(listFiles[1])
 exc<-read.csv(listFiles[2])
 
 #renaming exclusion values 3 -> 5 (exc), 4 -> 3 (pt naming based on inc run)
 exc$names <- mapvalues(exc$names, from=c("1","2","3","4","5"), to=c("1","2", "6","7","5"))
 
#add 2x number of images in Run1 to all exc onsets
 exc$onsets <- exc$onsets + lengthRun1
 
 #merge inc & exc into one file (fp_1 (across runs) = 1, fp_inc = 2, hi = 3, pt (across runs) = 4, fp_exc = 5, exc = 6)
 file <- rbind(inc, exc)

 #set directory and write file
 setwd(summary_files_folder_concat)
 write.csv(file, paste("summary_concat_cyb",subjList[i],".csv", sep=""), row.names = FALSE) }