---
title: "id.blocks_cyb1_newPT_excVfpVhi"
author: "TCheng"
date: "June 29, 2016"
output: html_document
---

# Theresa Cheng | Nandita Vijayakumar
# 6/29/2016
# This script identifies the wait period and initial block of fair play within the Cyberball inclusion run
# newPT: adjusting the onset of the participant throw regressor to begin when they catch the ball (WITHIN the initial fair play block only)

#########
#!!! Remember to run 'module add R' at the command line first
#########
#Paths are set to run locally, not on the grid.

```{r}
# LOAD PACKAGES
osuRepo<-'http://ftp.osuosl.org/pub/cran/'

#Check if the packages we need are installed, and if not, install them
if(!require(plyr)){
  install.packages('plyr',repos=osuRepo)
}
library(plyr)

if(!require(dplyr)){
  install.packages('dplyr',repos=osuRepo)
}
library(dplyr)
if(!require(tidyr)){
  install.packages('tidyr',repos=osuRepo)
}
library(tidyr)
if(!require(data.table)){
  install.packages('data.table',repos=osuRepo)
}
library(data.table)
if(!require(R.matlab)){
  install.packages('R.matlab',repos=osuRepo)
}

if(!require(chron)){
  install.packages('R.matlab',repos=osuRepo)
}
library(chron)
library(R.matlab)
```

```{r} 
# LOAD FILES
rm(list=ls())

#define folder locations
tds_folder<-'/Volumes/research/tds/'
labeled_cyberball_folder<-'fMRI/analysis/fx/multicond/cyberball/TDS2_labeled_cyb_data'
labeled_files_folder<-paste(tds_folder,labeled_cyberball_folder,sep='')
summary_cyberball_folder<-'fMRI/analysis/fx/multicond/cyberball/TDS2_cyb_summary/blocks/excFpHi'
summary_files_folder<-paste(tds_folder,summary_cyberball_folder,sep='')

setwd(labeled_files_folder)

#list the files 
listFiles<-list.files(labeled_files_folder,recursive=T, pattern='cyb.*_1.csv$')
```

```{r}
# READ IN EACH FILE AND CLEAN IT UP

for(j in 1:length(listFiles)) 
{
  setwd(labeled_files_folder)
  df<-read.csv(listFiles[j]) #read in the file
  timestamp<-as.character(df[1,2]) #change the timestamp into a character

  # Reformat Timestamp Into Hour, Minutes, and Seconds.Milliseconds
  df<-separate(df, "timestamp", c("date", "time"), sep=16)
  df<-separate(df, "time", c("time","junk"), sep=8)

  df<-separate(df,"milliseconds",c("junk","milliseconds"), sep=1)
  df$time<-paste(df$time, df$milliseconds, sep="")

  #Delete unnecessary variables
  df <- df[,-(5:7)]
  
  # Label each behavior type according to the following scheme:
    # 4: catch(player1) catch(player3) 
    # 3: throw(player1) throw(player3)
    # 2: connecting(time: 6)
    # 1: throw(player1-player2) throw(player3-player2) #throws to the subj
    # 0: throw(player1-player3)
    # 0: throw(player3-player1) 
  
  df$behavior.num<-mapvalues(df$behavior.type, c("catch(player1)", "catch(player3)","throw(player1)","throw(player3)", "connecting(time: 6)", "throw(player1-player2)",
                                                 "throw(player3-player2)", "throw(player1-player3)","throw(player3-player1)"),c(4,4,3,3,2,1,1,0,0)) 
  
  # Filter out unnecessary information (catches, participant throws) keep connecting time and all throws from player 1 or 3
  df.blockID<-filter(df, behavior.num==1| behavior.num==2|behavior.num==0)

#for(k in 1:NROW(df.blockID))
#{ df.blockID$block.sum2[k] = df.blockID$behavior.num2[k+4] + df.blockID$behavior.num2[k+3] + df.blockID$behavior.num2[k+2] + df.blockID$behavior.num2[k+1] + df.blockID$behavior.num2[k]}

# #k=10
# 
### ORIGINAL CONTINUITY RULE 
#   df.blockID2 <- df.blockID
#   df.blockID$cont.throws<-rep(0,NROW(df.blockID)) # generate regressor of non-participant throws in hi.block
#   
#   for(k in 4:NROW(df.blockID))
#           {if (df.blockID$behavior.num[k]==0 && df.blockID$behavior.num[k-1]==1 && df.blockID$behavior.num[k-2]==1 && df.blockID$behavior.num[k-3]==1) {
#             if (is.na(df.blockID$behavior.num[k+1]==1)) {
#              df.blockID$behavior.num[k]=1
#              df.blockID$cont.throws[k]=1}
#             else if (is.na(df.blockID$behavior.num[k+2]==1) && df.blockID$behavior.num[k+1]==1) {
#                 df.blockID$behavior.num[k]=1
#                 df.blockID$cont.throws[k]=1}
#             else if (is.na(df.blockID$behavior.num[k+3]==1) && df.blockID$behavior.num[k+1]==1 && df.blockID$behavior.num[k+2]==1) {
#               df.blockID$behavior.num[k]=1
#               df.blockID$cont.throws[k]=1}
#             else if (df.blockID$behavior.num[k+1]==1 && df.blockID$behavior.num[k+2]==1 && df.blockID$behavior.num[k+3]==1) {
#             df.blockID$behavior.num[k]=1
#             df.blockID$cont.throws[k]=1}
#             else{}
#           } else {}
# }            

# ### MODIFIED CONTINUITY RULE BELOW
#   df.blockID$split.cont<-rep(0,NROW(df.blockID)) # generate regressor of non-participant throws in hi.block
# 
# for(k in 4:NROW(df.blockID))
#           {if (df.blockID$behavior.num[k]==0 && df.blockID$behavior.num[k-1]==1 && df.blockID$behavior.num[k-2]==1 && df.blockID$behavior.num[k-3]==1) {
#             if (is.na(df.blockID$behavior.num[k+1]==1)) {
#              df.blockID$split.cont[k]=1}
#             else if (is.na(df.blockID$behavior.num[k+2]==1) && df.blockID$behavior.num[k+1]==1) {
#                 df.blockID$split.cont[k]=1
#                 df.blockID$split.cont[k+1]=2}
#             else if (is.na(df.blockID$behavior.num[k+3]==1) && df.blockID$behavior.num[k+1]==1 && df.blockID$behavior.num[k+2]==1) {
#               df.blockID$split.cont[k]=1
#               df.blockID$split.cont[k+1]=2
#               df.blockID$split.cont[k+2]=2}
#             else if (df.blockID$behavior.num[k+1]==1 && df.blockID$behavior.num[k+2]==1 && df.blockID$behavior.num[k+3]==1) {
#             df.blockID$split.cont[k]=1
#             df.blockID$split.cont[k+1]=2}
#             else{}
#           } else {}
# }         

# IDENTIFY CONTINUITY BLOCKS - THIS SHOULD GO BETWEEN HYPERINCLUSION AND INCLUSION

# # Created a "lag" column to identify boundaries
# df.blockID <- df.blockID %>% mutate(blocks.lag=lag(blocks,1), boundaries=blocks==blocks.lag, index=1:n() %>% as.numeric(df.blockID$index))
# 
# cont.info<-subset(df.blockID,df.blockID$cont==1)
# 
# cont.info<-subset(df.blockID, df.hi$secondtoss[1]==df.blockID$index |df.hi$secondtoss[2]==df.blockID$index |df.hi$secondtoss[3]==df.blockID$index |df.hi$secondtoss[4]==df.blockID$index |df.hi$secondtoss[5]==df.blockID$index)


# IDENTIFY HYPERINCLUSION (HI) BLOCKS
 
  # Identify blocks of hi
  tmp<-rle(as.vector(df.blockID$behavior.num)) #found the lengths of repeating conditions types in df$behavior.num
  df.blockID$blocks<-rep(tmp$lengths>=3 & tmp$values==1, times=tmp$lengths) #identified when condition types repeated 
  
  # Created a "lag" column to identify boundaries
  df.blockID <- df.blockID %>% mutate(blocks.lag=lag(blocks,1), boundaries=blocks==blocks.lag, index=1:n() %>% as.numeric(df.blockID$index))

# Filtered df.blockID based on the boundaries (i.e. first row) that begin HI blocks - threshold of 3 repeating throws (coded above) to the participant for start of Hi block
  df.hi<-filter(df.blockID, blocks==TRUE, boundaries==FALSE)
  df.hi$secondtoss<-df.hi$index +1 # found row number of the SECOND toss in the HI blocks
  
# Filtered df.blockID based on the SECOND toss in the hi block, which is what we want as an onsets time
hi.info<-subset(df.blockID, df.hi$secondtoss[1]==df.blockID$index |df.hi$secondtoss[2]==df.blockID$index |df.hi$secondtoss[3]==df.blockID$index |df.hi$secondtoss[4]==df.blockID$index |df.hi$secondtoss[5]==df.blockID$index |df.hi$secondtoss[6]==df.blockID$index)
  hi.info$start<-1
  
  # Filtered df.blockID based on the toss that terminates the hi block
  df.hi<-filter(df.blockID, blocks==FALSE, boundaries==FALSE)
  df.hi$start<-0
  
  # Identify the end of the last block  (could be hi or inc)
  last.toss<-df[NROW(df),]
  #last.toss$cont.throws<-0
  last.toss$blocks<-NA
  last.toss$blocks.lag<-NA
  last.toss$boundaries<-NA
  last.toss$index<-NROW(df)
  last.toss$start<-0
  hi.info<-rbind(hi.info,last.toss) #bananas
  
  # Combine starts and ends of hi block and sort by index
  hi.info<-rbind(hi.info,df.hi)
  hi.info<-hi.info[order(hi.info$index),]

# IDENTIFY INCLUSION (inc) BLOCKS 

# Identify start of first inclusion block - begins with the first throw
first.toss<-df.blockID[2,]
first.toss$start<-1

# Filter df.blockID to identify the STARTs of inclusion blocks (aka the end of hyperinclusion, marked by the first throw between computer players. If there is only one throw btwn comp players between hyper inclusion blocks, do NOT start an inclusion block (this is the split.cont trash regressor))
df.inc<-filter(df.blockID, blocks==FALSE, boundaries==FALSE) #split.cont removed
df.inc$start<-1

# Filter df.blockID to identify the ENDS of inclusion blocks (aka the start of hyperinclusion 2nd of at least 3 throws to the player)

  # Step 1: Filtered df.blockID based on the boundaries (i.e. first row) that begin HI blocks - threshold of 3 repeating throws (coded above) to the participant for start of Hi block
  df.hi<-filter(df.blockID, blocks==TRUE, boundaries==FALSE) #split.cont==0
  
  # Step 2: Found row number of the SECOND toss in the HI blocks
  df.hi$secondtoss<-df.hi$index +1 
  
  # Step 3. Add the ENDS of inclusion blocks into inc.info
  inc.info<-subset(df.blockID, df.hi$secondtoss[1]==df.blockID$index |df.hi$secondtoss[2]==df.blockID$index |df.hi$secondtoss[3]==df.blockID$index |df.hi$secondtoss[4]==df.blockID$index |df.hi$secondtoss[5]==df.blockID$index |df.hi$secondtoss[6]==df.blockID$index)
  inc.info$start<-0

# Identify the end of the last block (could be hi or inc)
last.toss<-df[NROW(df),]
#last.toss$split.cont<-0
last.toss$blocks<-NA
last.toss$blocks.lag<-NA
last.toss$boundaries<-NA
last.toss$index<-NROW(df)
last.toss$start<-0

# Combine and order inc.info with first and last toss info
  inc.info<-rbind(inc.info, df.inc, first.toss, last.toss) 
  inc.info<-inc.info[order(inc.info$index),]
  
#CREATE NAMES, ONSET AND durations 
  #Create names variable
  inc.info$names<-"inc"
  hi.info$names<-"hi"
  
  #Create onsets variable
  op<-options(digits.secs=3)
inc.info$onsets<-inc.info$time
  hi.info$onsets<-hi.info$time
  
  #Create durations variable
op<-options(digits.secs=5)
inc.info$time<-strptime(inc.info$time, format="%H:%M:%OS")
 op<-options(digits.secs=5)
df$time<-strptime(df$time,format="%H:%M:%OS")
options(op)
  
  for (i in 1:NROW(inc.info)) {
    if (inc.info$start[i] == 1) {
      inc.info$durations[i] = difftime(inc.info$time[i+1],inc.info$time[i],unit="secs")
      inc.info$onsets[i]=difftime(inc.info$time[i],df$time[1], unit="secs")
    } else if (inc.info$start[i] < 1) {
      inc.info$durations[i] = NA
      inc.info$onsets[i]=NA}
    }
  
  op<-options(digits.secs=5)
  hi.info$time<-strptime(hi.info$time, format="%H:%M:%OS")
  options(op)
  
  inc.info<-subset(inc.info, start==1)
 inc.info<-subset(inc.info, !is.na(inc.info$blocks))
  
  for (i in 1:NROW(hi.info)) {
    if (hi.info$start[i] == 1) {
      hi.info$durations[i] = difftime(hi.info$time[i+1],hi.info$time[i],unit="secs")
      hi.info$onsets[i]=difftime(hi.info$time[i],df$time[1], unit="secs")
    } else if (hi.info$start[i] < 1) {
      hi.info$durations[i] = NA
      hi.info$onsets[i]=NA}
    }
  
  hi.info<-subset(hi.info,start==1)
  hi.info<-subset(hi.info, !is.na(hi.info$blocks))
  hi.file<-hi.info[,c(2,13:15)]

#### CREATE fp_1.info INCLUDING ONLY THE FIRST ROW OF inc.info
  fp_1.info<-inc.info[1,]
  fp_1.file<-fp_1.info[,c(2,13:15)]
  fp_1.file$names='fp_1'
  
### 8/31 Create fp_inc.info, including fair play blocks beyond the first row of inc.info
  fp_inc.info=inc.info[2:NROW(inc.info),]
  fp_inc.file=fp_inc.info[,c(2,13:15)]
  fp_inc.file$names='fp_inc'
  
# # IDENTIFY FIVESECS CONDITION: BLOCKS LESS THAN 5secs
# for (l in 1:NROW(file)){
#   if(file$durations[l]<5) {
#     file$names[l]<-"fivesecs"
#   }else{}
# }

# IDENTIFY PARTICIPANT THROWS

# Generate variables that reflect the conditions one trial later
  df$behavior.num1 =lead(df$behavior.num)
  
  # Loop specifies that if there are fewer than 1 cyberball action following the catch by a subject, specify duration=0
  for(i in 1:NROW(df)){
      if (df$behavior.num[i]==4 & !(is.na(df$behavior.num1[i]))) {
        df$pt.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
        df$pt.durations[i]= difftime(df$time[i+1],df$time[i],unit="secs")}
      else if (df$behavior.num[i]==4 & is.na(df$behavior.num1[i])) {
        df$pt.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
        df$pt.durations[i]=0 }
        else {
        df$pt.onsets[i]=NA
        df$pt.durations[i]=NA}
      }
  
  pt.info<-subset(df,df$behavior.num==4)
  pt.info$names<-"pt"
  pt.info$onsets<-pt.info$pt.onsets
  #pt.info$durations<-pt.info$pt.durations
  pt.info$durations=rep(0, NROW(pt.info))
  
  pt.file<-pt.info[,c(2,11:13)]

### FP: Filter out onsets that began after the FP block
  #endFp=as.numeric(file$onsets)+as.numeric(file$durations)
  #pt.file=filter(pt.file, pt.file$onsets<endFp)
  
#### Reformat TIME in df.blockID
op<-options(digits.secs=5)
df.blockID$time<-strptime(df.blockID$time, format="%H:%M:%OS")
options(op)

# # MODEL ALL COMPUTER THROWS
#   for (l in 1:NROW(df.blockID)) {
#     if (df.blockID$behavior.num[l]==0 | df.blockID$behavior.num[l]==1) {
#       df.blockID$compt.onsets[l] = difftime(df.blockID$time[l],df$time[1],unit="secs")
#       df.blockID$compt.durations[l] = 0
#     } else {
#       df.blockID$compt.onsets[l]= NA
#       df.blockID$compt.durations[l]= NA
#     }
#   }
# 
# compt.info<-subset(df.blockID, df.blockID$behavior.num=="0" |df.blockID$behavior.num=="1") #subset out throws by the computer
# compt.info$names<-"compthrow"
# compt.info$onsets<-compt.info$compt.onsets
# compt.info$durations<-compt.info$compt.durations
# compt.file<-compt.info[,c(2,15,16,17)]

# "SPLIT CONTINUITY" ONSETS AND DURATIONS
#Create durations variable
#df.blockID$time<-strptime(df.blockID$time, format="%H:%M:%OS")
#options(op)
# 
# for (l in 1:NROW(df.blockID)) {
# if (df.blockID$split.cont[l]==1 && is.na(df.blockID$split.cont[l+1]==2)){
#   df.blockID$split.cont.onsets[l] = difftime(df.blockID$time[l],df$time[1],unit="secs")
#   df.blockID$split.cont.durations[l] = 0 
# } else if (df.blockID$split.cont[l]==1 && df.blockID$split.cont[l+1]==2 && (is.na(df.blockID$split.cont[l+2]==1))) {
#  df.blockID$split.cont.onsets[l] = difftime(df.blockID$time[l],df$time[1],unit="secs")
#   df.blockID$split.cont.durations[l] = difftime(df.blockID$time[l+1],df.blockID$time[l],unit="secs")
# } else if (df.blockID$split.cont[l]==1 && df.blockID$split.cont[l+1]==2 && df.blockID$split.cont[l+2]==2 && (is.na(df.blockID$split.cont[l+3]==1))){ 
#   df.blockID$split.cont.onsets[l] = difftime(df.blockID$time[l],df$time[1],unit="secs")
#   df.blockID$split.cont.durations[l] = difftime(df.blockID$time[l+2],df.blockID$time[l],unit="secs")
#   } else if (df.blockID$split.cont[l]==1 && df.blockID$split.cont[l+1]==2 && df.blockID$split.cont[l+2]==0) {
#   df.blockID$split.cont.onsets[l] = difftime(df.blockID$time[l],df$time[1],unit="secs")
#   df.blockID$split.cont.durations[l] = difftime(df.blockID$time[l+2],df.blockID$time[l],unit="secs")
# } else {
#   df.blockID$split.cont.onsets[l] = NA
#   df.blockID$split.cont.durations[l] = NA
# }}

# split.cont.info<-subset(df.blockID,(is.na(split.cont.onsets)==0))
# 
# X=NROW(split.cont.info)
# 
#   if (X>0) {
#   split.cont.info$names<-"splitcont"  
#   split.cont.info$onsets<-split.cont.info$split.cont.onsets
#   split.cont.info$durations<-split.cont.info$split.cont.durations
#   split.cont.info<-split.cont.info[,c(2,17,18,19)]
#   } else {
#     }

##IDENTIFY wait
  for(i in 1:NROW(df)){
    if (df$behavior.num[i]==2) {
      df$wait.onsets[i]=difftime(df$time[i],df$time[1], unit="secs")
      df$wait.durations[i]= difftime(df$time[i+1],df$time[i],unit="secs")}
    else {
      df$wait.onsets[i]=NA
      df$wait.durations[i]=NA}
  }

wait.info<-subset(df,!(is.na(df$wait.onsets)))
wait.info$names<-"wait"
wait.info$onsets<-wait.info$wait.onsets
wait.info$durations<-wait.info$wait.durations
wait.file<-wait.info[,c(2,13:15)]

#COMBINE wait, PT and FP INFO and SAVE CSV FILE
#   if (X>0) {
#     file<-rbind(file, pt.file)
#   } else {
#       file<-rbind(file,pt.file)}

file<-rbind(wait.file, fp_1.file, fp_inc.file, hi.file, pt.file)

  # change name into a numeral
  # 1: hi
  # 2: inc
  # 3: pt
  # 4: compthrow
  # 5: blocks5s/fivesecs AND split cont

file$names<-mapvalues(file$names,c("wait","fp_1","fp_inc","hi","pt"), c(1,2,3,4,5))
file$names<-as.numeric(file$names)
file$onsets<-as.numeric(file$onsets)
#file$durations<-mapvalues(file$durations,NA, 0)

# remove last catch
#file<-subset(file, durations!<0)

setwd(summary_files_folder)
write.csv(file, paste("summary_excFpHi",listFiles[j], sep="_"))

}
```