---
title: 'Characteristics of Early + Mid # of Gos'
author: "Theresa Cheng"
date: "August 23, 2016"
output: word_document
---

# This script loads, cleans, and plots data related to the number of Gos in early and mid yellow light game behavior ("EM"). It examines relationships between EM, age, sex, and RPI in preparation for a Flux 2016 conference poster.

# Load packages
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(sjPlot)
```

# Acquire data 
```{r}
rm(list=ls())

# Cyberball subject list
setwd("/Volumes/research/tds/behavioral/raw/cyberball")
subjectList=as.data.frame(read.csv("SubjectList_full.csv", header=FALSE), header=FALSE)
colnames(subjectList) = c("SID", "Age")

# Demographic data
setwd("/Users/theresacheng/Dropbox (PfeiBer Lab)/TDS/TDS-II/data/Qualtrics/Scored_Qualtrics/Session_2")
df_demo<-as.data.frame(read.csv("TDS2_S2_Qualtrics_2015.10.03.csv", header=TRUE))
df_demo<-df_demo[,c("SID","Age","Gender")]
  
# Trial-by-trial stoplight behavior
setwd("/Volumes/research/tds/behavioral/processed/ylg")
df_trial<-read.csv("tds2-all_trial_by_trial.csv", header=TRUE)

# Calculate the number of decisions per subject per run by intersection type
df_trial$decision=as.numeric(df_trial$decision) #make it into a numeric value; 3=stop, 1=go, 2= penalty 
numGo=summarise(group_by(df_trial, subject.name, run_index, type), sum(decision=="1")) 
colnames(numGo)=c("SID", "run","type", "numGo")

# Dealing with NAs, which make it so that the spread function doesn't work
  sum(is.na(numGo$type))
  numGo=numGo[-1408,]

numGo= spread(numGo, key=type, value=numGo)

# RPI data
setwd("/Volumes/research/tds/behavioral/processed/cyberball")
RPI<-read.csv("RPI.csv", header=TRUE)

```

# Manipulate data for this particular analysis
```{r}

# Subset demographic information by Cyberball subject list
df_demo=merge(subjectList, df_demo, by="SID")
df_demo$Age.y=NULL
colnames(df_demo)=c("SID", "age", "sex")

# Create a dataframe of Gos fo early + mid trials only
numGo$EM=numGo$E+numGo$M # merge the count for early and mid trials
df=cbind(numGo[,1:2], numGo[,6]) # create a dataframe of just these trials
df=spread(df, key=run, value=EM)

# Merge with demographic data
df=merge(df_demo, df)

# Create a long version for graphing funsies
df_long=gather(df, "run", "EM", 4:11)

# Generate variables of average num of Gos for each condition
df$aloneGo=(df$"3"+df$"4")/2
df$peerGo=(df$"5"+df$"6")/2
df$excGo=(df$"7"+df$"8")/2

# Missing data: 
# Note that 189 was removed for lacking ylg beh data
# 127 and 168 is missing run 8, use run 7 data as the excGo value
df[10,]$excGo=df[10,]$"7"
df[43,]$excGo=df[43,]$"7"

# subset df down to grouped variables
df[,4:11]=NULL

# generate difference scores
df$peer_alone=df$peerGo-df$aloneGo
df$exc_peer=df$excGo-df$peerGo
df$exc_alone=df$excGo-df$aloneGo

# remove 189 from RPI list
RPI=RPI[-61,]

# add RPI variable to the df
df$RPI=RPI$RPI_cov
```

# How do the number of Gos in early and middle intersections change by run?
```{r, warning=FALSE}
# Generate a summary dataframe
EMbyRun=summarise(group_by(df_long, run), mean(EM, na.rm=TRUE), se=sd(EM, na.rm=TRUE)/sqrt(length(EM)))
colnames(EMbyRun)=c("run", "mean", "se")

factor(EMbyRun$run, labels=c("Alone 1", "Alone 2", "Alone 3", "Alone 4", "Peer 1", "Peer 2", "Exclusion 1", "Exclusion 2"))

p=ggplot(data=EMbyRun, aes(x=run, y=mean)) + #plot it
 geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) +
  geom_point() +
  geom_line() +
  ggtitle("Go decisions Across Yellow Light Game Conditions") + 
  labs(x= "Condition", y="Average number of Go decisions")

p + scale_x_discrete(labels=c("Practice 1", "Practice 2", "Alone 1", "Alone 2", "Peer 1", "Peer 2", "Exclusion 1", "Exclusion 2"))

# This plot suggests that we should not lump across the alone trials (1-4), and that differences related to learning the task and/or the scanner environment make 3-4 qualitatively different. 
# Also, this graph suggests that collapsing across 34, 56, and 78 trials is reasonable
```

# How is ylg behavior in early+mid #Gos affected by age and sex?
## Descriptives
```{r}
# Inspect the data distributions
hist(df$aloneGo) #ylg beh
hist(df$peerGo)
hist(df$excGo)
hist(df$age) # age and gender
tally(df, sex)

# Inspect scatterplots 
plot(df$aloneGo, df$peerGo) #ylg beh
plot(df$aloneGo, df$excGo)
plot(df$peerGo, df$excGo)

plot(df$aloneGo, df$age) #ylg and age
plot(df$peerGo, df$age)
plot(df$excGo, df$age)

# Examine correlations
cor.table=cor(df)
sjt.corr(df, p.numeric=TRUE, corr.method="pearson")
```

## Regression models
```{r}
# Do age and sex significantly predict the number of Gos (examined by condition)?
M1 <- lm(aloneGo ~ age + sex, data=df) #alone
summary(M1)

M2 <- lm(peerGo ~ age + sex, data=df) #peer
summary(M2)

M3 <- lm(excGo ~ age + sex, data=df) #exc
summary(M3)

# Do age and sex significantly predict the differences in the number of Gos (examined by condition)?
M4 <- lm(peer_alone ~ age + sex, data=df) #peer minus alone
summary(M4) 

# Yes, graph this effect
ggplot(data=df, aes(x=age, y=peer_alone))+
  geom_point()+
  geom_smooth(method="lm") +
  ggtitle("Peer effect on early+mid intersections vs. age")

M5 <- lm(exc_peer ~ age + sex, data=df) #exc minus peer
summary(M5)

M6 <- lm(exc_alone ~ age + sex, data=df) #exc minus alone
summary(M6)
```

# Acquire difference scores between conditions in early and mid trials, plus peer minus alone scores with an age residual
```{r}
df$mc_age=scale(df$age, scale=FALSE)
df$mc_aloneGo=scale(df$aloneGo, scale=FALSE)
df$mcPeer_alone=scale(df$peer_alone, scale=FALSE)
df$mcExc_peer=scale(df$exc_peer, scale=FALSE)
df$mcExc_alone=scale(df$exc_alone, scale=FALSE)

setwd("/Volumes/research/tds/behavioral/processed/cyberball")
#write.csv(df, "ylgBeh_earlyMid.csv")

M7 <- lm(peer_alone ~ age, data=df) #peer minus alone
summary(M7) 
peer_alone_ageResid=as.data.frame(as.numeric(M7$residual))
colnames(peer_alone_ageResid)="peer_alone_ageResid"
peer_alone_ageResid$mcPeer_alone_ageResid=scale(peer_alone_ageResid, scale=FALSE)

#write.csv(peer_alone_ageResid, "peer_alone_ageResid.csv")
```

# Is the difference between Gos in the exclusion and peer conditions collinear with alone Gos?
```{r}
cor.test(df$exc_peer, df$aloneGo)
```

# Now let's think about RPI
```{r}
summary(M4) #peer minus alone by age + sex, presented for comparison

M5 <- lm(peer_alone ~ age + RPI + sex, data=df) #peer minus alone
summary(M5)

df_ofInterest= as.data.frame(cbind(df$age, df$sex, df$RPI, df$peer_alone))
colnames(df_ofInterest)= c("Age", "Sex","RPI","Peer Effect")

sjt.corr(df_ofInterest, p.numeric=TRUE, corr.method="pearson", no.output=TRUE)
cor.table2=cor(df_ofInterest)

```

