---
title: "explore_stoplight_beh"
author: "TC NV"
date: "April 20, 2016"
output: html_document
---

```{r}
# LOAD PACKAGES
osuRepo<-'http://ftp.osuosl.org/pub/cran/'

#Check if the packages we need are installed, and if not, install them
if(!require(plyr)){
  install.packages('plyr',repos=osuRepo)
}
library(plyr)

if(!require(dplyr)){
  install.packages('dplyr',repos=osuRepo)
}
library(dplyr)
if(!require(tidyr)){
  install.packages('tidyr',repos=osuRepo)
}
library(tidyr)
if(!require(data.table)){
  install.packages('data.table',repos=osuRepo)
}
library(data.table)
if(!require(R.matlab)){
  install.packages('R.matlab',repos=osuRepo)
}

if(!require(chron)){
  install.packages('R.matlab',repos=osuRepo)
}
library(chron)
library(R.matlab)
if(!require(knitr)){
  install.packages('R.matlab',repos=osuRepo)
}
library(knitr)
if(!require(PerformanceAnalytics)){
  install.packages('PerformanceAnalytics')
}
library(PerformanceAnalytics)
```

```{r, warning=FALSE, echo=FALSE, eval=FALSE} 
# LOAD FILES
rm(list=ls())

# Demographic data
setwd("/Users/marge/Dropbox (PfeiBer Lab)/TDS/TDS-II/data/Qualtrics/Scored_Qualtrics/Session_2")

demo_df<-as.data.frame(read.csv("TDS2_S2_Qualtrics_2015.10.03.csv", header=TRUE))
demo_df<-demo_df[,c("SID","Age","Gender")]

# Stoplight behavior 
setwd("/Volumes/research/tds/behavioral/cyberball/stoplight_beh")
df<-read.csv("stoplight_beh.csv", header=TRUE)
df<-df[1:87,]

# Average stoplight behavior
df[1:10,]=NA

df$G34=df$GO3+df$GO4
mean(df$G34, na.rm=TRUE)
sd(df$G34, na.rm=TRUE)
df$G56=df$GO6+df$GO6
mean(df$G56, na.rm=TRUE)
sd(df$G56, na.rm=TRUE)
df$GO8=as.numeric(as.character(df$GO8))
df$G78=df$GO7+df$GO8
mean(df$G78, na.rm=TRUE)
sd(df$G78, na.rm=TRUE)

df$FA34=df$FA3+df$FA4
df$FA56=df$FA5+df$FA5
df$FA8=as.numeric(as.character(df$FA8))
df$FA78=df$FA7+df$FA8

mean(df$FA34, na.rm=TRUE)
sd(df$FA34, na.rm=TRUE)
mean(df$FA56, na.rm=TRUE)
sd(df$FA56, na.rm=TRUE)
mean(df$FA78, na.rm=TRUE)
sd(df$FA78, na.rm=TRUE)

t.test(df$G34, df$G78, paired = TRUE, var.equal = TRUE)
 
df$SID<-df$SID1

df_all<-merge(demo_df, df, by = "SID")

# add subject IDs and merge demographics w/ stoplight behavior
setwd("/Volumes/research/tds/behavioral/cyberball")
df_age <-read.csv("SubjectList_full.csv", header=FALSE)
df_age$SID <- df_age$V1
df <- merge(df_age, df, by="SID")

# BRAIN
setwd("/Volumes/research/tds/rx/ROIs/cyb_events/catchonly_meanCpmod_linear/ROIs_definedBy_exc_p")
df_exc_ROIs_intercept<-read.csv("ROIs_summary_exc.csv", header=TRUE)
df_exc_ROIs<-read.csv("ROIs_summary_exc_p.csv", header=TRUE)
setwd("/Volumes/research/tds/rx/ROIs/cyb_events/catchonly_meanCpmod_linear/ROIs_definedBy_inc_p")
df_inc_ROIs_intercept<-read.csv("ROIs_summary_inc.csv", header=TRUE)
df_inc_ROIs<-read.csv("ROIs_summary_inc_p.csv", header=TRUE)
df_ROIs<-as.data.frame(bind_cols(df_exc_ROIs_intercept, df_exc_ROIs, df_inc_ROIs_intercept, df_inc_ROIs))
setwd("/Volumes/research/tds/rx/ROIs/cyb_events/catchonly_meanCpmod_linear/Exc_p_vs_Inc_p")
df_excVinc_ROIs<-read.csv("ROIs_summary_exc_p_vs_inc_p.csv", header=TRUE)
df_ROIs<-as.data.frame(bind_cols(df_exc_ROIs_intercept, df_exc_ROIs, df_inc_ROIs_intercept, df_inc_ROIs, df_excVinc_ROIs))

# remove randomly created variables (ick)
df_ROIs$X<-NULL
df_ROIs$X.1<-NULL
df_ROIs$X.2<-NULL
df_ROIs$X.3<-NULL

# MERGE
df<-as.data.frame(bind_cols(df,df_ROIs))
```

#EXCLUSION ANALYSES

Correlation: Go to brain
```{r, warning=FALSE}

#set up the dataframe
df_GoExcP<-as.data.frame(cbind(df$G12, df$G34, df$G56, df$G78, df$exc_p_ROI_n28n88n34, df$exc_p_ROI_n4420n10, df$exc_p_ROI_n58n6234, df$exc_p_ROI_n66n364,df$exc_p_ROI_04438, df$exc_p_ROI_28n80n36, df$exc_p_ROI_2n5862, df$exc_p_ROI_212n24, df$exc_p_ROI_462642, df$exc_p_ROI_4826n12, df$exc_p_ROI_56n24n8))

#rename columns
colnames(df_GoExcP)<-c("G12", "G34", "G56", "df$G78","exc_p_ROI_n28n88n34", "exc_p_ROI_n4420n10", "exc_p_ROI_n58n6234", "exc_p_ROI_n66n364", "exc_p_ROI_04438", "exc_p_ROI_28n80n36", "exc_p_ROI_2n5862", "exc_p_ROI_212n24", "exc_p_ROI_462642", "exc_p_ROI_4826n12", "exc_p_ROI_56n24n8")

chart.Correlation(df_GoExcP, histogram=FALSE)
```

differences in Go to brain
```{r, warning=FALSE}
df$dG78_34<-as.numeric(df$G78)-as.numeric(df$G34)

#set up the dataframe
df_dGoExcP<-as.data.frame(cbind(df$dG34_12, df$dG56_34, df$dG78_56, df$dG78_34, df$exc_p_ROI_n28n88n34, df$exc_p_ROI_n4420n10, df$exc_p_ROI_n58n6234, df$exc_p_ROI_n66n364, df$exc_p_ROI_04438, df$exc_p_ROI_28n80n36, df$exc_p_ROI_2n5862, df$exc_p_ROI_212n24, df$exc_p_ROI_462642, df$exc_p_ROI_4826n12, df$exc_p_ROI_56n24n8))

#rename columns
colnames(df_dGoExcP)<-c("dG34_12", "dG56_34", "dG78_56", "df$dG78_34","exc_p_ROI_n28n88n34", "exc_p_ROI_n4420n10", "exc_p_ROI_n58n6234", "exc_p_ROI_n66n364", "exc_p_ROI_04438", "exc_p_ROI_28n80n36", "exc_p_ROI_2n5862", "exc_p_ROI_212n24", "exc_p_ROI_462642", "exc_p_ROI_4826n12", "exc_p_ROI_56n24n8")

chart.Correlation(df_dGoExcP, histogram=FALSE)
```

good decisions to brain
```{r, warning=FALSE}

#set up the dataframe
df_GDExcP<-as.data.frame(cbind(df$GD12, df$GD34, df$GD56, df$GD78, df$exc_p_ROI_n28n88n34, df$exc_p_ROI_n4420n10, df$exc_p_ROI_n58n6234, df$exc_p_ROI_n66n364, df$exc_p_ROI_04438, df$exc_p_ROI_28n80n36, df$exc_p_ROI_2n5862, df$exc_p_ROI_212n24, df$exc_p_ROI_462642, df$exc_p_ROI_4826n12, df$exc_p_ROI_56n24n8))

#rename columns
colnames(df_GDExcP)<-c("GD12", "GD34", "GD56", "df$GD78","exc_p_ROI_n28n88n34", "exc_p_ROI_n4420n10", "exc_p_ROI_n58n6234", "exc_p_ROI_n66n364", "exc_p_ROI_04438", "exc_p_ROI_28n80n36", "exc_p_ROI_2n5862", "exc_p_ROI_212n24", "exc_p_ROI_462642", "exc_p_ROI_4826n12", "exc_p_ROI_56n24n8")

chart.Correlation(df_GDExcP, histogram=FALSE)
```

differences in good decisions to brain
```{r, warning=FALSE}
df$dGD78_34<-as.numeric(df$GD78)-as.numeric(df$GD34)

#set up the dataframe
df_dGDExcP<-as.data.frame(cbind(df$dGD34_12, df$dGD56_34, df$dGD78_56, df$dGD78_34, df$exc_p_ROI_n28n88n34, df$exc_p_ROI_n4420n10, df$exc_p_ROI_n58n6234, df$exc_p_ROI_n66n364, df$exc_p_ROI_04438, df$exc_p_ROI_28n80n36, df$exc_p_ROI_2n5862, df$exc_p_ROI_212n24, df$exc_p_ROI_462642, df$exc_p_ROI_4826n12, df$exc_p_ROI_56n24n8))

#rename columns
colnames(df_dGDExcP)<-c("dGD34_12", "dGD56_34", "dGD78_56", "df$dGD78_34","exc_p_ROI_n28n88n34", "exc_p_ROI_n4420n10", "exc_p_ROI_n58n6234", "exc_p_ROI_n66n364", "exc_p_ROI_04438", "exc_p_ROI_28n80n36", "exc_p_ROI_2n5862", "exc_p_ROI_212n24", "exc_p_ROI_462642", "exc_p_ROI_4826n12", "exc_p_ROI_56n24n8")

chart.Correlation(df_dGDExcP, histogram=FALSE)
```

bad decisions to brain
```{r, warning=FALSE}
#set up the dataframe
df_BDExcP<-as.data.frame(cbind(df$BD12, df$BD34, df$BD56, df$BD78, df$exc_p_ROI_n28n88n34, df$exc_p_ROI_n4420n10, df$exc_p_ROI_n58n6234, df$exc_p_ROI_n66n364, df$exc_p_ROI_04438, df$exc_p_ROI_28n80n36, df$exc_p_ROI_2n5862, df$exc_p_ROI_212n24, df$exc_p_ROI_462642, df$exc_p_ROI_4826n12, df$exc_p_ROI_56n24n8))

#rename columns
colnames(df_BDExcP)<-c("BD12", "BD34", "BD56", "df$BD78","exc_p_ROI_n28n88n34", "exc_p_ROI_n4420n10", "exc_p_ROI_n58n6234", "exc_p_ROI_n66n364", "exc_p_ROI_04438", "exc_p_ROI_28n80n36", "exc_p_ROI_2n5862", "exc_p_ROI_212n24", "exc_p_ROI_462642", "exc_p_ROI_4826n12", "exc_p_ROI_56n24n8")

chart.Correlation(df_BDExcP, histogram=FALSE)
```

differences in bad decisions to brain
```{r, warning=FALSE}
df$dBD78_34<-as.numeric(df$BD78)-as.numeric(df$BD34)

#set up the dataframe
df_dBDExcP<-as.data.frame(cbind(df$dBD34_12, df$dBD56_34, df$dBD78_56, df$dBD78_34, df$exc_p_ROI_n28n88n34, df$exc_p_ROI_n4420n10, df$exc_p_ROI_n58n6234, df$exc_p_ROI_n66n364, df$exc_p_ROI_04438, df$exc_p_ROI_28n80n36, df$exc_p_ROI_2n5862, df$exc_p_ROI_212n24, df$exc_p_ROI_462642, df$exc_p_ROI_4826n12, df$exc_p_ROI_56n24n8))

#rename columns
colnames(df_dBDExcP)<-c("dBD34_12", "dBD56_34", "dBD78_56", "df$dBD78_34","exc_p_ROI_n28n88n34", "exc_p_ROI_n4420n10", "exc_p_ROI_n58n6234", "exc_p_ROI_n66n364", "exc_p_ROI_04438", "exc_p_ROI_28n80n36", "exc_p_ROI_2n5862", "exc_p_ROI_212n24", "exc_p_ROI_462642", "exc_p_ROI_4826n12", "exc_p_ROI_56n24n8")

chart.Correlation(df_dBDExcP, histogram=FALSE)
```

crashes (false alarms) to brain
```{r, warning=FALSE}
#set up the dataframe
df_FAExcP<-as.data.frame(cbind(df$FA12, df$FA34, df$FA56, df$FA78, df$exc_p_ROI_n28n88n34, df$exc_p_ROI_n4420n10, df$exc_p_ROI_n58n6234, df$exc_p_ROI_n66n364, df$exc_p_ROI_04438, df$exc_p_ROI_28n80n36, df$exc_p_ROI_2n5862, df$exc_p_ROI_212n24, df$exc_p_ROI_462642, df$exc_p_ROI_4826n12, df$exc_p_ROI_56n24n8))

#rename columns
colnames(df_FAExcP)<-c("FA12", "FA34", "FA56", "df$FA78","exc_p_ROI_n28n88n34", "exc_p_ROI_n4420n10", "exc_p_ROI_n58n6234", "exc_p_ROI_n66n364", "exc_p_ROI_04438", "exc_p_ROI_28n80n36", "exc_p_ROI_2n5862", "exc_p_ROI_212n24", "exc_p_ROI_462642", "exc_p_ROI_4826n12", "exc_p_ROI_56n24n8")

chart.Correlation(df_FAExcP, histogram=FALSE)
```

differences in crashes (false alarms) to brain
```{r, warning=FALSE}
df$dFA78_34<-as.numeric(df$FA78)-as.numeric(df$FA34)

#set up the dataframe
df_dFAExcP<-as.data.frame(cbind(df$dFA34_12, df$dFA56_34, df$dFA78_56, df$dFA78_34, df$exc_p_ROI_n28n88n34, df$exc_p_ROI_n4420n10, df$exc_p_ROI_n58n6234, df$exc_p_ROI_n66n364, df$exc_p_ROI_04438, df$exc_p_ROI_28n80n36, df$exc_p_ROI_2n5862, df$exc_p_ROI_212n24, df$exc_p_ROI_462642, df$exc_p_ROI_4826n12, df$exc_p_ROI_56n24n8))

#rename columns
colnames(df_dFAExcP)<-c("dFA34_12", "dFA56_34", "dFA78_56", "df$dFA78_34","exc_p_ROI_n28n88n34", "exc_p_ROI_n4420n10", "exc_p_ROI_n58n6234", "exc_p_ROI_n66n364", "exc_p_ROI_04438", "exc_p_ROI_28n80n36", "exc_p_ROI_2n5862", "exc_p_ROI_212n24", "exc_p_ROI_462642", "exc_p_ROI_4826n12", "exc_p_ROI_56n24n8")

chart.Correlation(df_dFAExcP, histogram=FALSE)
```

misses
```{r, warning=FALSE}
#set up the dataframe
df_MIExcP<-as.data.frame(cbind(df$MI12, df$MI34, df$MI56, df$MI78, df$exc_p_ROI_n28n88n34, df$exc_p_ROI_n4420n10, df$exc_p_ROI_n58n6234, df$exc_p_ROI_n66n364, df$exc_p_ROI_04438, df$exc_p_ROI_28n80n36, df$exc_p_ROI_2n5862, df$exc_p_ROI_212n24, df$exc_p_ROI_462642, df$exc_p_ROI_4826n12, df$exc_p_ROI_56n24n8))

#rename columns
colnames(df_MIExcP)<-c("MI12", "MI34", "MI56", "df$MI78","exc_p_ROI_n28n88n34", "exc_p_ROI_n4420n10", "exc_p_ROI_n58n6234", "exc_p_ROI_n66n364", "exc_p_ROI_04438", "exc_p_ROI_28n80n36", "exc_p_ROI_2n5862", "exc_p_ROI_212n24", "exc_p_ROI_462642", "exc_p_ROI_4826n12", "exc_p_ROI_56n24n8")

chart.Correlation(df_MIExcP, histogram=FALSE)
```

differences in misses to brain
```{r, warning=FALSE}
df$dMI78_34<-as.numeric(df$MI78)-as.numeric(df$MI34)

#set up the dataframe
df_dMIExcP<-as.data.frame(cbind(df$dMI34_12, df$dMI56_34, df$dMI78_56, df$dMI78_34, df$exc_p_ROI_n28n88n34, df$exc_p_ROI_n4420n10, df$exc_p_ROI_n58n6234, df$exc_p_ROI_n66n364, df$exc_p_ROI_04438, df$exc_p_ROI_28n80n36, df$exc_p_ROI_2n5862, df$exc_p_ROI_212n24, df$exc_p_ROI_462642, df$exc_p_ROI_4826n12, df$exc_p_ROI_56n24n8))

#rename columns
colnames(df_dMIExcP)<-c("dMI34_12", "dMI56_34", "dMI78_56", "df$dMI78_34","exc_p_ROI_n28n88n34", "exc_p_ROI_n4420n10", "exc_p_ROI_n58n6234", "exc_p_ROI_n66n364", "exc_p_ROI_04438", "exc_p_ROI_28n80n36", "exc_p_ROI_2n5862", "exc_p_ROI_212n24", "exc_p_ROI_462642", "exc_p_ROI_4826n12", "exc_p_ROI_56n24n8")

chart.Correlation(df_dMIExcP, histogram=FALSE)
```

#INCLUSION

Gos
```{r, warning=FALSE}
#set up the dataframe
df_GIncP<-as.data.frame(cbind(df$G12, df$G34, df$G56, df$G78,df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_GIncP)<-c("G12", "G34", "G56", "df$G78","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_GIncP, histogram=FALSE)
```

difference in gos
```{r, warning=FALSE}
df$dG78_34<-as.numeric(df$G78)-as.numeric(df$G34)

#set up the dataframe
df_dGIncP<-as.data.frame(cbind(df$dG34_12, df$dG56_34, df$dG78_56, df$dG78_34, df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434, df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_dGIncP)<-c("dG34_12", "dG56_34", "dG78_56", "df$dG78_34","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_dGIncP, histogram=FALSE)
```

good outcomes
```{r, warning=FALSE}
#set up the dataframe
df_GDIncP<-as.data.frame(cbind(df$GD12, df$GD34, df$GD56, df$GD78,df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_GDIncP)<-c("GD12", "GD34", "GD56", "df$GD78","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_GDIncP, histogram=FALSE)
```

difference in good outcomes
```{r, warning=FALSE}
df$dGD78_34<-as.numeric(df$GD78)-as.numeric(df$GD34)

#set up the dataframe
df_dGDIncP<-as.data.frame(cbind(df$dGD34_12, df$dGD56_34, df$dGD78_56, df$dGD78_34, df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434, df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_dGDIncP)<-c("dGD34_12", "dGD56_34", "dGD78_56", "df$dGD78_34","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_dGDIncP, histogram=FALSE)
```

bad outcomes
```{r, warning=FALSE}
#set up the dataframe
df_BDIncP<-as.data.frame(cbind(df$BD12, df$BD34, df$BD56, df$BD78,df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_BDIncP)<-c("BD12", "BD34", "BD56", "df$BD78","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_BDIncP, histogram=FALSE)
```

differences in bad outcomes
```{r, warning=FALSE}
df$dBD78_34<-as.numeric(df$BD78)-as.numeric(df$BD34)

#set up the dataframe
df_dBDIncP<-as.data.frame(cbind(df$dBD34_12, df$dBD56_34, df$dBD78_56, df$dBD78_34, df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_dBDIncP)<-c("dBD34_12", "dBD56_34", "dBD78_56", "df$dBD78_34","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_dBDIncP, histogram=FALSE)
```

crashes
```{r, warning=FALSE}
#set up the dataframe
df_FAIncP<-as.data.frame(cbind(df$FA12, df$FA34, df$FA56, df$FA78,df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_FAIncP)<-c("FA12", "FA34", "FA56", "df$FA78","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_FAIncP, histogram=FALSE)
```

differences in crashes
```{r, warning=FALSE}
df$dFA78_34<-as.numeric(df$FA78)-as.numeric(df$FA34)

#set up the dataframe
df_dFAIncP<-as.data.frame(cbind(df$dFA34_12, df$dFA56_34, df$dFA78_56, df$dFA78_34, df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_dFAIncP)<-c("dFA34_12", "dFA56_34", "dFA78_56", "df$dFA78_34","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_dFAIncP, histogram=FALSE)
```

misses
```{r, warning=FALSE}
#set up the dataframe
df_MIIncP<-as.data.frame(cbind(df$MI12, df$MI34, df$MI56, df$MI78,df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_MIIncP)<-c("MI12", "MI34", "MI56", "df$MI78","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_MIIncP, histogram=FALSE)
```

differences in misses to brain
```{r, warning=FALSE}
df$dMI78_34<-as.numeric(df$MI78)-as.numeric(df$MI34)

#set up the dataframe
df_dMIIncP<-as.data.frame(cbind(df$dMI34_12, df$dMI56_34, df$dMI78_56, df$dMI78_34, df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_dMIIncP)<-c("dMI34_12", "dMI56_34", "dMI78_56", "df$dMI78_34","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_dMIIncP, histogram=FALSE)
```

# SUBTRACTION

Gos
```{r, warning=FALSE}
#set up the dataframe
df_GIncP<-as.data.frame(cbind(df$G12, df$G34, df$G56, df$G78,df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_GIncP)<-c("G12", "G34", "G56", "df$G78","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_GIncP, histogram=FALSE)
```

difference in gos
```{r, warning=FALSE}
df$dG78_34<-as.numeric(df$G78)-as.numeric(df$G34)

#set up the dataframe
df_dGIncP<-as.data.frame(cbind(df$dG34_12, df$dG56_34, df$dG78_56, df$dG78_34, df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434, df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_dGIncP)<-c("dG34_12", "dG56_34", "dG78_56", "df$dG78_34","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_dGIncP, histogram=FALSE)
```

good outcomes
```{r, warning=FALSE}
#set up the dataframe
df_GDIncP<-as.data.frame(cbind(df$GD12, df$GD34, df$GD56, df$GD78,df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_GDIncP)<-c("GD12", "GD34", "GD56", "df$GD78","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_GDIncP, histogram=FALSE)
```

difference in good outcomes
```{r, warning=FALSE}
df$dGD78_34<-as.numeric(df$GD78)-as.numeric(df$GD34)

#set up the dataframe
df_dGDIncP<-as.data.frame(cbind(df$dGD34_12, df$dGD56_34, df$dGD78_56, df$dGD78_34, df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434, df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_dGDIncP)<-c("dGD34_12", "dGD56_34", "dGD78_56", "df$dGD78_34","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_dGDIncP, histogram=FALSE)
```

bad outcomes
```{r, warning=FALSE}
#set up the dataframe
df_BDIncP<-as.data.frame(cbind(df$BD12, df$BD34, df$BD56, df$BD78,df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_BDIncP)<-c("BD12", "BD34", "BD56", "df$BD78","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_BDIncP, histogram=FALSE)
```

differences in bad outcomes
```{r, warning=FALSE}
df$dBD78_34<-as.numeric(df$BD78)-as.numeric(df$BD34)

#set up the dataframe
df_dBDIncP<-as.data.frame(cbind(df$dBD34_12, df$dBD56_34, df$dBD78_56, df$dBD78_34, df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_dBDIncP)<-c("dBD34_12", "dBD56_34", "dBD78_56", "df$dBD78_34","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_dBDIncP, histogram=FALSE)
```

crashes
```{r, warning=FALSE}
#set up the dataframe
df_FAIncP<-as.data.frame(cbind(df$FA12, df$FA34, df$FA56, df$FA78,df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_FAIncP)<-c("FA12", "FA34", "FA56", "df$FA78","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_FAIncP, histogram=FALSE)
```

differences in crashes
```{r, warning=FALSE}
df$dFA78_34<-as.numeric(df$FA78)-as.numeric(df$FA34)

#set up the dataframe
df_dFAIncP<-as.data.frame(cbind(df$dFA34_12, df$dFA56_34, df$dFA78_56, df$dFA78_34, df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_dFAIncP)<-c("dFA34_12", "dFA56_34", "dFA78_56", "df$dFA78_34","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_dFAIncP, histogram=FALSE)
```

misses
```{r, warning=FALSE}
#set up the dataframe
df_MIIncP<-as.data.frame(cbind(df$MI12, df$MI34, df$MI56, df$MI78,df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_MIIncP)<-c("MI12", "MI34", "MI56", "df$MI78","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_MIIncP, histogram=FALSE)
```

differences in misses to brain
```{r, warning=FALSE}
df$dMI78_34<-as.numeric(df$MI78)-as.numeric(df$MI34)

#set up the dataframe
df_dMIIncP<-as.data.frame(cbind(df$dMI34_12, df$dMI56_34, df$dMI78_56, df$dMI78_34, df$inc_p_ROI_n30n88n30, df$inc_p_ROI_n5228n12, df$inc_p_ROI_04434,df$inc_p_ROI_18n102_14, df$inc_p_ROI_42n80n30, df$inc_p_ROI_4630n16, df$inc_p_ROI_56n22n8))

#rename columns
colnames(df_dMIIncP)<-c("dMI34_12", "dMI56_34", "dMI78_56", "df$dMI78_34","inc_p_ROI_n30n88n30", "inc_p_ROI_n5228n12", "inc_p_ROI_04434","inc_p_ROI_18n102_14", "inc_p_ROI_42n80n30", "inc_p_ROI_4630n16", "inc_p_ROI_56n22n8")

chart.Correlation(df_dMIIncP, histogram=FALSE)
```



