---
title: "graphROIs"
author: "TC NV"
date: "April 22, 2016"
output: html_document
---

# Theresa Cheng | Nandita Vijayakumar
# 4/22/2016
# This script generates graphs for the linear & linear+quadratic functions of an ROI (threshold: 0.0005, 159 voxels, 48, 26, -12/vlPFC)


```{r}
# LOAD PACKAGES
osuRepo<-'http://ftp.osuosl.org/pub/cran/'

#Check if the packages we need are installed, and if not, install them
if(!require(plyr)){
  install.packages('plyr',repos=osuRepo)
}
library(plyr)

if(!require(dplyr)){
  install.packages('dplyr',repos=osuRepo)
}
library(dplyr)
if(!require(tidyr)){
  install.packages('tidyr',repos=osuRepo)
}
library(tidyr)
if(!require(data.table)){
  install.packages('data.table',repos=osuRepo)
}
library(data.table)
if(!require(R.matlab)){
  install.packages('R.matlab',repos=osuRepo)
}

if(!require(chron)){
  install.packages('R.matlab',repos=osuRepo)
}
library(chron)
library(R.matlab)
library(ggplot2)
```

```{r} 
# LOAD FILES
rm(list=ls())

setwd("/Volumes/research/tds/rx/ROIs/cyb_events")

exc<-read.csv("exc_summary_timecourse.csv", header=FALSE)
exc_p<-read.csv("exc_p_summary_timecourse.csv", header=FALSE)
  exc_p2<-read.csv("exc_p2_summary_timecourse.csv", header=FALSE)

avg_exc<-mean(exc[,1])
avg_p<-mean(exc_p[,1])
avg_p2<-mean(exc_p2[,1])

x_lin<--4:7
x_quad<-x_lin^2

df_avg<-as.data.frame(matrix(c(x_lin,rep(avg_exc,12),avg_p*x_lin, avg_p2*x_quad), nrow=12))
colnames(df_avg)= c("pmod", "intercept","linear","quadratic")

ggplot(df_avg, aes(x=pmod, y=intercept+linear)) +
  geom_point(shape=1) +
  geom_smooth()+
  geom_smooth(aes(x=pmod, y=intercept+linear+quadratic))
  
ggplot(df_avg, aes(x=pmod, y=intercept+linear+quadratic))+
  geom_point(shape=1) +
  geom_smooth()

