###############
## Data prep ##
###############
```{r}
##Check if the packages we need are installed, and if not, install them
packages<-c('dplyr', 'tidyr', 'data.table', 'R.matlab', 'ggplot2', 'lme4')
if(length(setdiff(packages, rownames(installed.packages())))>0) {
  install.packages(setdiff(packages, rownames(installed.packages())))
}
lapply(packages, library, character.only=TRUE)

##Set paths (data is located on psi-svr-filer)
tds_folder<-'/Volumes/TDS/behavior/'
ylg_folder<-paste(tds_folder, 'YLG/processed/', sep='')
demo_folder<-paste(tds_folder, 'Redcap/', sep='')
qualtrics_folder<-paste(tds_folder, 'Qualtrics/', sep='')

##Collect data
ylg_data<-read.csv(paste(ylg_folder,'tds-all_trial_by_trial.csv',sep=''))
demo_data<-read.csv(paste(demo_folder,'age_gender_iq.csv',sep=''))
qualtrics_data<-read.csv(paste(qualtrics_folder, 'scoring_script_output/TDS-2-auto_scored_scales_wide.csv', sep=''))
```
#######################
## Demographics N=81 ##
#######################
```{r}
# Select Qualtrics data needed
qualtrics_data_selection <- qualtrics_data %>% select(starts_with("SID"), starts_with("PDS"))

#change names to be easier to read later
names(demo_data) <- c("SID", "age", "gender", "iq")
## Merge qualtrics and demo data
demo <- merge(demo_data, qualtrics_data_selection, by.x = 'SID', by.y = 'SID')


## Add variables
demo <- demo %>%
  mutate(age_group = ifelse(age < 14.0, 1, 2)) %>% # age groups based on median split
  mutate(age_c = age-14.1, age_rnd = floor(age), age_sq = age_c^2) %>%   # age variables
  mutate(iq_c = iq-100, iq_z = iq_c/15) %>%                   # iq variables
  mutate(PDS_mean_score=ifelse(                               # pds variables
    is.na(PDS_female_mean_score_score)==TRUE, PDS_male_mean_score_score, PDS_female_mean_score_score)) %>%
  mutate(PDS_stage = ceiling(PDS_mean_score), pds_group = ifelse(PDS_mean_score < 2.9, 1, 2)) %>%
  mutate(gender_flip = ifelse(gender==0, 'Male', 'Female'))   # flip gender for correct colors in graph

## Filter demo_data (N=81)
no_session2 = c(118, 123, 147, 148, 149, 153, 154, 166, 180)
behaviorals = c(103, 107, 112, 138, 143, 176, 191)
demo_filtered <- demo %>% filter(SID < 300) %>% 
  filter(!SID %in% no_session2) %>% 
  filter(!SID %in% behaviorals)

#demo_filtered %>% group_by(age_group) %>% summarize(n=n()) # n for each age group
#demo_filtered %>% group_by(pds_group) %>% summarize(n=n())

#PDS_mean_scores <- demo_filtered %>% distinct(SID, gender, PDS_pds_gender_score, PDS_mean_score) %>% filter(!grepl("189|158|160|174", SID)) 
#write.csv(PDS_mean_scores, file = 'tds2_PDS_mean_score_n77.csv')
```
#############
## TABLE 1 PAPER 1##
#############
```{r}
# Age by gender
age_by_sex<-demo_filtered %>% filter(!is.na(age)) %>% group_by(gender) %>% 
  summarize(mean = mean(age, na.rm=T), sd = sd(age, na.rm=T), 
            min = min(age, na.rm=T), max = max(age, na.rm=T),
            n = n(), se = sd/sqrt(n), ci=qt(0.975, df=n-1)*se) # n=42 females
t.test(demo_filtered$age~demo_filtered$gender) #t = -0.87254, df = 78.303, p-value = 0.3856 (m=13.9, f=14.2)

# IQ by gender
iq_by_sex<-demo_filtered %>% filter(!is.na(iq)) %>% group_by(gender) %>% 
  summarize(mean = mean(iq, na.rm=T), sd = sd(iq, na.rm=T), 
            min = min(iq, na.rm=T), max = max(iq, na.rm=T),
            n = n(), se = sd/sqrt(n), ci=qt(0.975, df=n-1)*se)
t.test(demo_filtered$iq~demo_filtered$gender) #t = 0.05078, df = 78.04, p-value = 0.9596 (m=107.2, f=107.1)

# PDS score by gender
pds_by_sex<-demo_filtered %>% filter(!is.na(PDS_mean_score)) %>% group_by(gender) %>% 
  summarize(mean = mean(PDS_mean_score, na.rm=T), sd = sd(PDS_mean_score, na.rm=T),
            min = min(PDS_mean_score, na.rm=T), max = max(PDS_mean_score, na.rm=T),
            n = n(), se = sd/sqrt(n), ci=qt(0.975, df=n-1)*se)
t.test(demo_filtered$PDS_mean_score~demo_filtered$gender) #t = -5.3362, df = 76.876, p-value = 9.286e-07 (m=2.4, f=3.1)
```
####################################
## SUPPLEMENTARY FIGURE S1 PAPER 1##
####################################
```{r}
# Part A: Gender by age distribution
fig_s1a <- ggplot(demo_filtered, aes(x = age_rnd, fill = gender_flip)) +
  geom_bar(position = 'dodge') +
  #facet_grid(.~tds_group, scales='free', labeller=as_labeller(group_labels)) +
  labs(x='Age', y='Number of participants', fill='Sex') +
  coord_cartesian(x=c(10.5,17.5)) + theme(text = element_text(size=16)) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10)) + scale_x_continuous(breaks = 11:17) 
ggsave('fig_s1a.png', fig_s1a)

# Part B: Gender by pubertal stage distribution
fig_s1b <- ggplot(demo_filtered, aes(x = PDS_stage, fill = gender_flip)) +
  geom_bar(position = 'dodge') +
  #facet_grid(.~tds_group, scales='free', labeller=as_labeller(group_labels)) +
  labs(x='Mean PDS score', y='Number of participants', fill='Sex') +
  theme(text = element_text(size=16)) +
  scale_y_continuous(breaks = c(0, 4, 8, 12, 16, 20, 24, 28)) + scale_x_continuous(breaks = c(1, 2, 3, 4))
ggsave('fig_s1b.png', fig_s1b)
```
##################
## YLG behavior ##
##################
```{r}
# Add variables

ylg = ylg_data %>% 
  mutate(condition = ifelse(grepl('1|2', run_index), 1,
                     ifelse(grepl('3|4', run_index), 2,
                     ifelse(grepl('5|6', run_index), 3, 
                     ifelse(grepl('7|8', run_index), 4, NA))))) %>%
  mutate(time=run.time.ms/60000) %>%
  mutate(go = ifelse(decision=='GO', 1, 0)) %>%
  mutate(crash = ifelse(scenario=='CRASH', 1, 0)) %>%
  mutate(go_cr = ifelse(decision=='GO' & scenario=='CRASH', 1, 0)) %>%
  mutate(stop = ifelse(decision=='STOP', 1, 0)) %>%
  mutate(stop_nocar = ifelse(decision=='STOP' & scenario=='SAFE', 1, 0)) %>%
  mutate(event = ifelse(decision=='GO' & scenario=='SAFE', 1,
                 ifelse(decision=='GO' & scenario=='CRASH', 2,
                 ifelse(decision=='STOP' & scenario=='CROSSCAR', 3,
                 ifelse(decision=='STOP' & scenario=='SAFE', 4, NA))))) %>%
  mutate(count1 = ifelse(event==1, 1, 0)) %>%
  mutate(count2 = ifelse(event==2, 1, 0)) %>%
  mutate(count3 = ifelse(event==3, 1, 0)) %>%
  mutate(count4 = ifelse(event==4, 1, 0))

ylg$SID <- ylg$subject.name 
# Check if events are present for all subjects
# events_by_sid <- ylg %>% group_by(SID, condition) %>%
#   summarize(n_good.go = sum(count1, na.rm=TRUE),
#             n_bad.go = sum(count2, na.rm=TRUE),
#             n_good.stop = sum(count3, na.rm=TRUE),
#             n_bad.stop = sum(count4, na.rm=TRUE))
# write.csv(events_by_sid, "/Volumes/TDS/behavior/YLG/processed/tds_events_by_sid.csv")

# Convert to factors
ylg$run_index <- as.factor(ylg$run_index)
ylg$condition <- as.factor(ylg$condition)

# Filter out subjects for imaging results (N=80)
# 301-399 = TDS-1
# 401-499 = TDS-3
# >500 = YADS
# 189 = incomplete dataset and excessive head motion
# 158 = excessive dropout
# 139 = excessive head motion during stop 7+8
# 103, 107, 112, 138, 143, 176, 191 = behavioral
# 101, 102, 104, 105, 106, 108, 110, 111 = completed old Cyberball version (no hyperinclusion)
exclude = c(189, 158, 139, 103, 107, 112, 138, 143, 176, 191, 101, 102, 104, 105, 106, 108, 110, 111)
ylg_filtered = ylg %>% filter(SID < 300) %>% 
  filter(!SID %in% exclude)
count_trials_per_sub<-ylg_filtered %>% group_by(SID) %>% summarize(n()) 
# 127 only has 140 trials (practice run 2 is missing) 

# Set labels
condition_labels = c(`1`='Mock', `2`='Alone', `3`='Peer Incl', `4`='Peer Excl')

# Dataset for behavioral analyses 
df <- merge(demo_filtered, ylg_filtered, by = 'SID')

# Dataset for analyses involving PDS
df_pds <- df %>% filter(!is.na(PDS_mean_score))

# Set as factors
df$gender <- as.factor(df$gender)
df$gender_flip <- as.factor(df$gender_flip)
```
###############################################
## Social Context effects on GO DECISIONS ##
###############################################
```{r}

#to compare within scanner social contexts
df_fMRI <- df %>% filter(condition != "1")


# Run effects on the proportion of Go decisions
null.model <- glmer(go ~ (1|SID), data=df_fMRI, family='binomial')
run.model <- glmer(go ~ run_index + (1|SID), data=df_fMRI, family='binomial')
anova(null.model, run.model)     
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
# null.model  2 10848 10862 -5422.0    10844                             
# run.model   7 10816 10865 -5400.9    10802 42.077      5  5.682e-08 ***
summary(run.model) 
# Fixed effects:
#              Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.614565   0.093395  -6.580  4.7e-11 ***                    
# run_index4  -0.003331   0.081517  -0.041   0.9674    
# run_index5   0.185894   0.080759   2.302   0.0213 *  
# run_index6   0.153758   0.080869   1.901   0.0573 .  
# run_index7   0.316061   0.080427   3.930  8.5e-05 ***
# run_index8   0.403818   0.080282   5.030  4.9e-07 ***

#Teens took significantly more risks (go decisions) in the first run following peer inclusion, and both runs following social exclusion. 

# Condition effects on the proportion of Go decisions
null.model <- glmer(go ~ (1|SID), data=df_fMRI, family='binomial')
condition.model <- glmer(go ~ condition + (1|SID), data=df_fMRI, family='binomial')
anova(null.model, condition.model)  
#                 Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
# null.model       2 10848 10862 -5422.0    10844                             
# condition.model  4 10811 10839 -5401.6    10803 40.686      2  1.462e-09 ***
summary(condition.model)  
#  Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.61621    0.08402  -7.334 2.24e-13 ***
# condition3   0.17151    0.05715   3.001  0.00269 ** 
# condition4   0.36169    0.05684   6.364 1.97e-10 ***

#Teens took significantly more risks (go decisions) in both social contexts than when they played alone.

social_df <- df_fMRI %>% filter(condition != "2")
null.model <- glmer(go ~ (1|SID), data=social_df, family='binomial')
condition.model <- glmer(go ~ condition + (1|SID), data=social_df, family='binomial')
anova(null.model, condition.model)  
#                Df    AIC    BIC  logLik deviance Chisq Chi Df Pr(>Chisq)    
# null.model       2 7349.4 7362.6 -3672.7   7345.4                            
# condition.model  3 7340.0 7359.9 -3667.0   7334.0 11.37      1  0.0007464 ***
summary(condition.model) 
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.44144    0.08211  -5.376  7.6e-08 ***
# condition4   0.18959    0.05622   3.372 0.000745 ***

#when compare social, still signficantly more go decisions following social exclusion.
```
################################################
## Social Context effects on CRASHES (BAD GO) ##
################################################
```{r}
# Run effects on the proportion of Go decisions that resulted in Crashes
null.model <- glmer(go_cr ~ (1|SID), data=df_fMRI, family='binomial')
run.model <- glmer(go_cr ~ run_index + (1|SID), data=df_fMRI, family='binomial', control=glmerControl(optimizer="bobyqa"))
anova(null.model, run.model) 
#            Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)  
# null.model  2 8372.8 8386.8 -4184.4   8368.8                           
# run.model   7 8371.1 8420.4 -4178.6   8357.1 11.634      5    0.04017 *
summary(run.model) 
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.56110    0.08932 -17.477  < 2e-16 ***
# run_index4   0.09086    0.09751   0.932  0.35148    
# run_index5   0.12316    0.09709   1.269  0.20461    
# run_index6   0.10478    0.09733   1.077  0.28170    
# run_index7   0.24691    0.09556   2.584  0.00978 ** 
# run_index8   0.27239    0.09528   2.859  0.00425 **

#Teens had significantly more bad go outcomes (crashes) following social exlcusion than when they played alone.

# Condition effects on the proportion of Go decisions that resulted in Crashes
null.model <- glmer(go_cr ~ (1|SID), data=df_fMRI, family='binomial')
condition.model <- glmer(go_cr ~ condition + (1|SID), data=df_fMRI, family='binomial')
anova(null.model, condition.model)         
#                 Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)   
# null.model       2 8372.8 8386.8 -4184.4   8368.8                            
# condition.model  4 8366.1 8394.2 -4179.0   8358.1 10.657      2    0.00485 **
summary(condition.model) 
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.51506    0.07395 -20.486  < 2e-16 ***
# condition3   0.06796    0.06827   0.996  0.31947    
# condition4   0.21366    0.06699   3.189  0.00143 ** 

#This pattern was confirmed when collapsed across runs within social context: teens take more risks following social exlusions.


null.model <- glmer(go_cr ~ (1|SID), data=social_df, family='binomial')
condition.model <- glmer(go_cr ~ condition + (1|SID), data=social_df, family='binomial')
anova(null.model, condition.model)         
#                 Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)  
# null.model       2 5720.5 5733.7 -2858.2   5716.5                           
# condition.model  3 5717.7 5737.6 -2855.8   5711.7 4.7872      1    0.02867 *
summary(condition.model) 
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.43677    0.06956 -20.656   <2e-16 ***
# condition4   0.14512    0.06618   2.193   0.0283 *  

#and within social contexts, increased following social exclusion
```
###############################################
## Social Context effects on STOP DECISIONS ##
###############################################
```{r}
# Run effects on the proportion of Stop decisions
null.model <- glmer(stop ~ (1|SID), data=df_fMRI, family='binomial')
run.model <- glmer(stop ~ run_index + (1|SID), data=df_fMRI, family='binomial')
anova(null.model, run.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
# null.model  2 10981 10995 -5488.5    10977                             
# run.model   7 10959 11008 -5472.4    10945 32.067      5  5.762e-06 ***
summary(run.model)
# Fixed effects:
#              Estimate Std. Error z value Pr(>|z|)    
# (Intercept)  0.443987   0.092989   4.775 1.80e-06 ***
# run_index4  -0.006464   0.080302  -0.080 0.935847    
# run_index5  -0.146898   0.079905  -1.838 0.066003 .  
# run_index6  -0.112044   0.079988  -1.401 0.161289    
# run_index7  -0.278814   0.079684  -3.499 0.000467 ***
# run_index8  -0.350520   0.079625  -4.402 1.07e-05 ***

#Coversely, teens signficantly stop less following both social exlusion compared to playing alone.

## Condition effects on the proportion of Stop decisions
null.model <- glmer(stop ~ (1|SID), data=df_fMRI, family='binomial')
condition.model <- glmer(stop ~ condition + (1|SID), data=df_fMRI, family='binomial')
anova(null.model, condition.model)
#                 Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
# null.model       2 10981 10995 -5488.5    10977                             
# condition.model  4 10954 10982 -5472.9    10946 31.045      2  1.814e-07 ***
summary(condition.model) 
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept)  0.44074    0.08385   5.256 1.47e-07 ***
# condition3  -0.12626    0.05652  -2.234   0.0255 *  
# condition4  -0.31146    0.05632  -5.530 3.21e-08 ***

#Collapsed across runs within social context, however, teens stop more in both social context, than they do when they play alone.


null.model <- glmer(stop ~ (1|SID), data=social_df, family='binomial')
condition.model <- glmer(stop ~ condition + (1|SID), data=social_df, family='binomial')
anova(null.model, condition.model)
#                 Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
# null.model       2 7402.0 7415.2 -3699.0   7398.0                             
# condition.model  3 7393.1 7413.0 -3693.5   7387.1 10.901      1   0.000961 ***

summary(condition.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept)  0.31236    0.08295   3.766 0.000166 ***
# condition4  -0.18484    0.05598  -3.302 0.000960 ***

#confirming within social context signfincatly decrease stops following social exlcusion
```
#######################################################################################
## Social Context effects on Stop decisions when there was no crossing car (BAD STOP)##
#######################################################################################
```{r}
# Run effects on the proportion of Bad Stop decisions
null.model <- glmer(stop_nocar ~ (1|SID), data=df_fMRI, family='binomial')
run.model <- glmer(stop_nocar ~ run_index + (1|SID), data=df_fMRI, family='binomial')
anova(null.model, run.model)
#            Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)  
# null.model  2 9870.5 9884.6 -4933.3   9866.5                           
# run.model   7 9866.6 9915.9 -4926.3   9852.6 13.888      5    0.01634 *
summary(run.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.88032    0.06969 -12.632  < 2e-16 ***
# run_index4   0.02083    0.08326   0.250  0.80244    
# run_index5  -0.12512    0.08452  -1.480  0.13878    
# run_index6  -0.05997    0.08393  -0.715  0.47491    
# run_index7  -0.16214    0.08488  -1.910  0.05611 .  
# run_index8  -0.24198    0.08572  -2.823  0.00476 ** 

#This pattern is also reflected in less correct stops (good stop outcome/car in intersection) in the last social exlcusion run than alone.

# Condition effects on the proportion of Stop decisions
null.model <- glmer(stop_nocar ~ (1|SID), data=df_fMRI, family='binomial')
condition.model <- glmer(stop_nocar ~ condition + (1|SID), data=df_fMRI, family='binomial')
anova(null.model, condition.model)
#                 Df    AIC    BIC  logLik deviance Chisq Chi Df Pr(>Chisq)   
# null.model       2 9870.5 9884.6 -4933.3   9866.5                           
# condition.model  4 9862.1 9890.3 -4927.1   9854.1  12.4      2   0.002029 **

summary(condition.model) 
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.86988    0.05576 -15.602  < 2e-16 ***
# condition3  -0.10275    0.05949  -1.727  0.08413 .  
# condition4  -0.21212    0.06025  -3.521  0.00043 ***

#this was confirmed when runs were collapsed across social context.

#within social bad stops 
null.model <- glmer(stop_nocar ~ (1|SID), data=social_df, family='binomial')
condition.model <- glmer(stop_nocar ~ condition + (1|SID), data=social_df, family='binomial')
anova(null.model, condition.model)
#                 Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)  
# null.model       2 6478.7 6491.9 -3237.3   6474.7                           
# condition.model  3 6477.4 6497.3 -3235.7   6471.4 3.2252      1    0.07251 

summary(null.model) 

# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept)  -1.0263     0.0479  -21.43   <2e-16 ***

#however, number of bad stops did not signifcantly increase between two social conditions.
```


#####################################################################
## FIGURE 1: Social Context by run effects on Task Behavior ##
#####################################################################
```{r}
# Part A: Run and Condition effects on Go decisions
go_by_sid = df_fMRI %>% group_by(SID, run_index, condition) %>% summarize(mean_go = mean(go))
plot_group_go = go_by_sid %>% group_by(run_index, condition) %>% summarize(mean=mean(mean_go), 
                                                                    sd=sd(mean_go), 
                                                                    n=70, # entered manually (could not be calculated because 127 has 140 trials, whereas all other subjects have 160 trials)
                                                                    se=sd/sqrt(n), 
                                                                    ci=qt(0.975, df=n-1)*se) 
  
fig_2a <- ggplot(plot_group_go, aes(x = run_index, y = mean, group=1)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci)) +
  facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
  labs(x='Run number', y='Propotion of Go decisions') 
  theme(text = element_text(size=18), axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14), strip.text.x = element_text(size=18)) 
ggsave('fig_2a.png', fig_2a)

# Part B: Run and Location effects on Crashes
go_cr_by_sid = df_fMRI %>% group_by(SID, run_index, condition) %>% summarize(mean_go_cr = mean(go_cr))
plot_group_go_cr = go_cr_by_sid %>% group_by(run_index, condition) %>% summarize(mean = mean(mean_go_cr), 
                                                                    sd = sd(mean_go_cr), 
                                                                    n=70, # entered manually (could not be calculated because 127 has 140 trials, whereas all other subjects have 160 trials)
                                                                    se=sd/sqrt(n), 
                                                                    ci=qt(0.975, df=n-1)*se) 

fig_2b <- ggplot(plot_group_go_cr, aes(x = run_index, y = mean, group=1)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci)) +
  facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
  labs(x='Run number', y='Propotion of Go decisions\nthat resulted in Crashes') 
  theme(text = element_text(size=18), axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14), strip.text.x = element_text(size=18)) 
ggsave('fig_2b.png', fig_2b)

# Part C: Run and Location effects on Stop decisions
stop_by_sid = df_fMRI %>% group_by(SID, run_index, condition) %>% summarize(mean_stop = mean(stop))
plot_group_stop = stop_by_sid %>% group_by(run_index, condition) %>% summarize(mean = mean(mean_stop), 
                                                                    sd = sd(mean_stop), 
                                                                    n=70, # entered manually (could not be calculated because 127 has 140 trials, whereas all other subjects have 160 trials)
                                                                    se=sd/sqrt(n), 
                                                                    ci=qt(0.975, df=n-1)*se) 

fig_2c <- ggplot(plot_group_stop, aes(x = run_index, y = mean, group=1)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci)) +
  facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
  labs(x='Run number', y='Propotion of Stop decisions') 
  theme(text = element_text(size=18), axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14), strip.text.x = element_text(size=18)) 
ggsave('fig_2c.png', fig_2c)

# Part d: Run and Location effects on Bad Stop decisions
stop_nocar_by_sid = df_fMRI %>% group_by(SID, run_index, condition) %>% summarize(mean_stop_nocar = mean(stop_nocar))
plot_group_stop_nocar = stop_nocar_by_sid %>% group_by(run_index, condition) %>% summarize(mean = mean(mean_stop_nocar), 
                                                                    sd = sd(mean_stop_nocar), 
                                                                    n=70, # entered manually (could not be calculated because 127 has 140 trials, whereas all other subjects have 160 trials)
                                                                    se=sd/sqrt(n), 
                                                                    ci=qt(0.975, df=n-1)*se) 

fig_2d <- ggplot(plot_group_stop_nocar, aes(x = run_index, y = mean, group=1)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci)) +
  facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
  labs(x='Run number', y='Propotion of Bad Stop decisions') 
  theme(text = element_text(size=18), axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14), strip.text.x = element_text(size=18)) 
ggsave('fig_2d.png', fig_2d)
```


###############################################################
## Social Context effects on GO DECISIONS W/ RW RISK BEHAVIOR##
###############################################################
```{r}
RWR_qualtrics_data <- qualtrics_data %>% select(SID, RPI_part2_rpi_mean_score, NTS_total_score_score, BIS.15_bis_total_score, B.SSS_sss_total_score, SPSRQ.S_sensitivity_punishment_mean_score, SPSRQ.S_sensitivity_reward_mean_score)

no_session2 = c(118, 123, 147, 148, 149, 153, 154, 166, 180)
behaviorals = c(103, 107, 112, 138, 143, 176, 191)
RWR_filtered <- RWR_qualtrics_data %>% filter(SID < 300) %>% 
  filter(!SID %in% no_session2) %>% 
  filter(!SID %in% behaviorals)


library(summarytools)
#check ranges of variables first
view(dfSummary(RWR_filtered))

df_RWR_fMRI <- left_join(df_fMRI, RWR_qualtrics_data, by= "SID")



```

# TASK CORRELATIONS RISK WITH RWB
```{r}
#are risk decisions in the scanner correlated with impuslivity and sensation seeking out of the scanner?
null.model <- aov(BIS.15_bis_total_score ~ go + (1|SID), data=df_RWR_fMRI)
main.model <- aov(BIS.15_bis_total_score ~ go + condition + (1|SID), data=df_RWR_fMRI)
interaction.model <- aov(BIS.15_bis_total_score ~ go*condition + (1|SID), data=df_RWR_fMRI)
anova(null.model, main.model)
anova(null.model, interaction.model)
summary(null.model)

#               Df Sum Sq Mean Sq F value  Pr(>F)   
# go             1    1.6  1.5682   7.335 0.00678 **
# Residuals   8158 1744.2  0.2138  

#increased impulsivity, increased gos across context.

null.model <- aov(B.SSS_sss_total_score ~ go + (1|SID), data=df_RWR_fMRI)
main.model <- aov(B.SSS_sss_total_score ~ go + condition + (1|SID), data=df_RWR_fMRI)
interaction.model <- aov(B.SSS_sss_total_score ~ go*condition + (1|SID), data=df_RWR_fMRI)
anova(null.model, main.model)
anova(null.model, interaction.model)
summary(null.model)
#               Df Sum Sq Mean Sq F value Pr(>F)
# go             1    0.0 0.00400   0.048  0.827
# Residuals   8158  683.8 0.08382  

#but not linked to sensation seeking


#do individual differences in sensitivity to reward, punishment correlated with changes in risk decisions across contexts?
null.model <- aov(SPSRQ.S_sensitivity_reward_mean_score ~ go + (1|SID), data=df_RWR_fMRI)
main.model <- aov(SPSRQ.S_sensitivity_reward_mean_score ~ go + condition + (1|SID), data=df_RWR_fMRI)
interaction.model <- aov(SPSRQ.S_sensitivity_reward_mean_score ~ go*condition + (1|SID), data=df_RWR_fMRI)
anova(null.model, main.model)
anova(null.model, interaction.model)
summary(null.model)
#               Df Sum Sq Mean Sq F value Pr(>F)
# go             1    0.1 0.05376   0.881  0.348
# Residuals   8398  512.4 0.06101  

#nope! 

null.model <- aov(SPSRQ.S_sensitivity_punishment_mean_score ~ go + (1|SID), data=df_RWR_fMRI)
main.model <- aov(SPSRQ.S_sensitivity_punishment_mean_score ~ go + condition + (1|SID), data=df_RWR_fMRI)
interaction.model <- aov(SPSRQ.S_sensitivity_punishment_mean_score ~ go*condition + (1|SID), data=df_RWR_fMRI)
anova(null.model, main.model)
anova(null.model, interaction.model)
summary(null.model)
#               Df Sum Sq Mean Sq F value Pr(>F)  
# go             1    0.2 0.20121   3.415 0.0646 .
# Residuals   8398  494.7 0.05891           

#nope!

null.model <- aov(NTS_total_score_score ~ go + (1|SID), data=df_RWR_fMRI)
main.model <- aov(NTS_total_score_score ~ go + condition + (1|SID), data=df_RWR_fMRI)
interaction.model <- aov(NTS_total_score_score ~ go*condition + (1|SID), data=df_RWR_fMRI)
anova(null.model, main.model)
anova(null.model, interaction.model)
summary(null.model)
#               Df Sum Sq Mean Sq F value   Pr(>F)    
# go             1      8   7.639   14.75 0.000123 ***
# Residuals   8278   4286   0.518                    

#increased go's across all conditions linked increased needs threat. 

null.model <- aov(RPI_part2_rpi_mean_score ~ go + (1|SID), data=df_RWR_fMRI)
main.model <- aov(RPI_part2_rpi_mean_score ~ go + condition + (1|SID), data=df_RWR_fMRI)
interaction.model <- aov(RPI_part2_rpi_mean_score ~ go*condition + (1|SID), data=df_RWR_fMRI)
anova(null.model, main.model)
anova(null.model, interaction.model)
summary(null.model)

#               Df Sum Sq Mean Sq F value Pr(>F)  
# go             1    0.9  0.8587   3.875  0.049 *
# Residuals   8398 1860.9  0.2216  

#increased resistance to peer influence in linked to increased go's across conditions, but doesn't survive multiple comparison.

```


###########################################################################################################
SUPPLEMENTAL 
###########################################################################################################


################################################################
## Age effects on GO DECISIONS while controlling for Sex & IQ ##
################################################################
```{r}
# Linear Age effects on the proportion of Go decisions (by run_index)
null.model <- glmer(go ~ run_index + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
main.model <- glmer(go ~ age_c + run_index + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
interaction.model <- glmer(go ~ age_c * run_index + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model  9 10819 10882 -5400.5    10801                         
# main.model 10 10821 10891 -5400.5    10801 0.0643      1     0.7998
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model         9 10819 10882 -5400.5    10801                         
# interaction.model 15 10821 10926 -5395.3    10791 10.281      6     0.1133


summary(null.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.53076    0.13057  -4.065 4.80e-05 ***
# run_index4  -0.00333    0.08152  -0.041   0.9674    
# run_index5   0.18590    0.08076   2.302   0.0213 *  
# run_index6   0.15376    0.08087   1.901   0.0573 .  
# run_index7   0.31606    0.08042   3.930 8.49e-05 ***
# run_index8   0.40383    0.08028   5.030 4.89e-07 ***
# gender1     -0.13364    0.15369  -0.870   0.3846    
# iq_z        -0.02588    0.09934  -0.261   0.7944 

#increase risk decisions across social context was not driven by age, controlling for IQ and gender

# Linear Age effects on the proportion of Go decisions (by location)
null.model <- glmer(go ~ condition + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
main.model <- glmer(go ~ age_c + condition + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
interaction.model <- glmer(go ~ age_c * condition + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model  6 10814 10857 -5401.2    10802                         
# main.model  7 10816 10866 -5401.2    10802 0.0643      1     0.7998
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model         6 10814 10857 -5401.2    10802                         
# interaction.model  9 10815 10878 -5398.6    10797 5.1947      3     0.1581

summary(null.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.53242    0.12406  -4.292 1.77e-05 ***
# condition3   0.17151    0.05715   3.001  0.00269 ** 
# condition4   0.36170    0.05684   6.364 1.97e-10 ***
# gender1     -0.13363    0.15371  -0.869  0.38465    
# iq_z        -0.02588    0.09932  -0.261  0.79441  

#finding confirmed when collapsed across runs
```
###############
## FIGURE 4A ##
###############
```{r}
#Part A: Go decisions plotted against Age
df_fMRI$pred_go <- predict(interaction.model, newdata=df_fMRI, re.form=NA, type='response')

fig_4a <- ggplot(data=df_fMRI, aes(x=age, y=pred_go, color=condition)) +
  geom_line(aes(group=condition), size=1) +
  labs(x='Age', y='Predicted probability of Go decisions', color='Condition') +
  theme(text = element_text(size=16)) +
  scale_colour_discrete(labels=condition_labels)
ggsave('fig_4a.png', fig_4a)

pGo <- df_fMRI %>% group_by(SID, condition) %>% summarize(pGo = mean(go))
pGo_by_age <- merge(pGo, demo, by = 'SID')

ggplot(pGo_by_age, aes(x = age, y = pGo, color=condition), stat_smooth(method = loess)) +
  geom_point() +
  geom_line(aes(group=condition), size=1) +
  #geom_errorbar(aes(ymax=mean + ci, ymin=mean - ci), width=0.5, position=position_dodge(.2)) +
  #facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
  labs(x='Age (mean-centered)', y='Proportion of Go decisions', color='Social Context')
```
######################################################################
## Age Group effects on GO DECISIONS while controlling for Sex & IQ ##
######################################################################
```{r}
# Age group effects on the proportion of Go decisions (by run_index)
# null.model <- glmer(go ~ run_index + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
# main.model <- glmer(go ~ age_group + run_index + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
# interaction.model <- glmer(go ~ age_group * run_index + gender + iq_z + (1|SID), data=df_fMRI, family='binomial', control=glmerControl(optimizer="bobyqa"))
# 
# anova(null.model, main.model)
# anova(null.model, interaction.model)
# anova(main.model, interaction.model)
# 
# summary(null.model)
# 
# # Age group effects on the proportion of Go decisions (by location)
# null.model <- glmer(go ~ condition + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
# main.model <- glmer(go ~ age_group + condition + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
# interaction.model <- glmer(go ~ age_group * condition + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
# 
# anova(null.model, main.model)
# anova(null.model, interaction.model)
# anova(main.model, interaction.model)
# 
# summary(null.model)
```
###########################################################
## Age effects on CRASHES while controlling for Sex & IQ ##
###########################################################
```{r}
# Age effects on the proportion of Go decisions that resulted in Crashes (by run_index)
null.model <- glmer(go_cr ~ run_index + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
main.model <- glmer(go_cr ~ age_c + run_index + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
interaction.model <- glmer(go_cr ~ age_c * run_index + gender + iq_z + (1|SID), data=df_fMRI, family='binomial', control=glmerControl(optimizer="bobyqa"))

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model 11 11111 11191 -5544.3    11089                         
# main.model 12 11113 11200 -5544.3    11089 0.0121      1     0.9124
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model        11 11111 11191 -5544.3    11089                         
# interaction.model 19 11114 11253 -5538.0    11076 12.617      8     0.1257
#anova(main.model, interaction.model)

summary(null.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.43537    0.10940 -13.121   <2e-16 ***
# run_index2   0.02410    0.09631   0.250   0.8024    
# run_index3  -0.07655    0.09762  -0.784   0.4329    
# run_index4   0.01396    0.09631   0.145   0.8847    
# run_index5   0.04615    0.09588   0.481   0.6303    
# run_index6   0.02783    0.09612   0.290   0.7721    
# run_index7   0.16941    0.09433   1.796   0.0725 .  
# run_index8   0.19479    0.09404   2.071   0.0383 *  
# gender1     -0.09179    0.11380  -0.807   0.4199    
# iq_z         0.01449    0.07332   0.198   0.8433  

# Age effects on the proportion of Go decisions that resulted in Crashes (by location)
null.model <- glmer(go_cr ~ condition + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
main.model <- glmer(go_cr ~ age_c + condition + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')
interaction.model <- glmer(go_cr ~ age_c * condition + gender + iq_z + (1|SID), data=df_fMRI, family='binomial')

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model  7 11104 11155 -5544.8    11090                         
# main.model  8 11106 11164 -5544.8    11090 0.0121      1     0.9125
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model         7 11104 11155 -5544.8    11090                         
# interaction.model 11 11109 11190 -5543.7    11087 2.3199      4     0.6772
# anova(main.model, interaction.model)

summary(null.model)
#Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.42335    0.09822 -14.491   <2e-16 ***
# condition2  -0.04274    0.06848  -0.624   0.5325    
# condition3   0.02496    0.06781   0.368   0.7128    
# condition4   0.17009    0.06652   2.557   0.0106 *  
# gender1     -0.09174    0.11381  -0.806   0.4202    
# iq_z         0.01450    0.07332   0.198   0.8433
```
###############
## FIGURE 4B ##
###############
```{r}
# Part B: Crashes
crashes <- df_fMRI %>% distinct(SID, gender_flip, condition, run_index, crash.count)
# new.row = c(127, 'Male', 1, 2, NA)
# crashes <- rbind(crashes, new.row)

plot.crashes <- crashes %>% group_by(gender_flip, condition, run_index) %>%
  summarize(mean = mean(crash.count), sd = sd(crash.count), n = n(), se = sd/sqrt(n), ci=qt(0.975, df=n-1)*se)

ggplot(plot.crashes, aes(x = run_index, y = mean, color=gender_flip)) +
  geom_point(position=position_dodge(.1), size=3) +
  geom_line(aes(group=gender_flip), size=1) +
  # geom_errorbar(aes(ymax=mean + ci, ymin=mean - ci), width=0.5, position=position_dodge(.2)) +
  # facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
  labs(x='Run number', y='Crashes', color='Sex') +
  scale_y_continuous(breaks = c(3, 4, 5))
```

####################################################################
## Puberty effects on GO DECISIONS while controlling for Sex & IQ ##
####################################################################
```{r}
df_pds <- df_fMRI %>% filter(!is.na(PDS_mean_score))
# Puberty effects on the proportion of Go decisions (by run_index)
null.model <- glmer(go ~ run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial')
main.model <- glmer(go ~ PDS_mean_score + run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))
interaction.model <- glmer(go ~ PDS_mean_score * run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance Chisq Chi Df Pr(>Chisq)
# null.model  9 10487 10550 -5234.7    10469                        
# main.model 10 10489 10559 -5234.4    10469 0.445      1     0.5047
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model         9 10487 10550 -5234.7    10469                         
# interaction.model 15 10493 10598 -5231.5    10463 6.3907      6     0.3809

summary(null.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.56796    0.13210  -4.300 1.71e-05 ***
# run_index4  -0.01723    0.08294  -0.208 0.835482    
# run_index5   0.18190    0.08208   2.216 0.026677 *  
# run_index6   0.15538    0.08217   1.891 0.058649 .  
# run_index7   0.31613    0.08170   3.869 0.000109 ***
# run_index8   0.40007    0.08154   4.906 9.28e-07 ***
# gender1     -0.08054    0.15549  -0.518 0.604464    
# iq_z        -0.04814    0.09995  -0.482 0.630102 

# Puberty effects on the proportion of Go decisions (by social context)
null.model <- glmer(go ~ condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
main.model <- glmer(go ~ PDS_mean_score + condition + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))
interaction.model <- glmer(go ~ PDS_mean_score * condition + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance Chisq Chi Df Pr(>Chisq)
# null.model  6 10483 10525 -5235.3    10471                        
# main.model  7 10484 10533 -5235.1    10470 0.445      1     0.5047
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model         6 10483 10525 -5235.3    10471                         
# interaction.model  9 10484 10548 -5233.2    10466 4.0586      3     0.2552


summary(null.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.57656    0.12544  -4.596 4.30e-06 ***
# condition3   0.17725    0.05811   3.051  0.00228 ** 
# condition4   0.36678    0.05776   6.350 2.15e-10 ***
# gender1     -0.08053    0.15547  -0.518  0.60447    
# iq_z        -0.04812    0.09993  -0.482  0.63015 
```
###############################################################
## Puberty effects on CRASHES while controlling for Sex & IQ ##
###############################################################
```{r}
# Puberty effects on the proportion of Go decisions that resulted in Crashes (by run_index)
null.model <- glmer(go_cr ~ run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))
main.model <- glmer(go_cr ~ PDS_mean_score + run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))
interaction.model <- glmer(go_cr ~ PDS_mean_score * run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))

anova(null.model, main.model)
#            Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model  9 8074.5 8137.6 -4028.3   8056.5                         
# main.model 10 8076.4 8146.5 -4028.2   8056.4 0.1533      1     0.6954
anova(null.model, interaction.model)
#                   Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model         9 8074.5 8137.6 -4028.3   8056.5                         
# interaction.model 15 8081.2 8186.3 -4025.6   8051.2 5.3768      6     0.496


summary(null.model)
# Fixed effects:
#              Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.538043   0.117611 -13.077  < 2e-16 ***
# run_index4   0.084497   0.099418   0.850  0.39537    
# run_index5   0.108573   0.099088   1.096  0.27320    
# run_index6   0.098982   0.099221   0.998  0.31848    
# run_index7   0.242156   0.097381   2.487  0.01289 *  
# run_index8   0.273006   0.097018   2.814  0.00489 ** 
# gender1     -0.062726   0.125214  -0.501  0.61641    
# iq_z        -0.002918   0.080250  -0.036  0.97100

# Puberty effects on the proportion of Go decisions that resulted in Crashes (by social context)
null.model <- glmer(go_cr ~ condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
main.model <- glmer(go_cr ~ PDS_mean_score + condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
interaction.model <- glmer(go_cr ~ PDS_mean_score * condition + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))

anova(null.model, main.model)
#            Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model  6 8069.4 8111.4 -4028.7   8057.4                         
# main.model  7 8071.2 8120.3 -4028.6   8057.2 0.1533      1     0.6954
anova(null.model, interaction.model)
#                   Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model         6 8069.4 8111.4 -4028.7   8057.4                         
# interaction.model  9 8074.3 8137.4 -4028.2   8056.3 1.0652      3     0.7855

summary(null.model) 
# Fixed effects:
#              Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.495263   0.105993 -14.107  < 2e-16 ***
# condition3   0.061003   0.069663   0.876  0.38120    
# condition4   0.214861   0.068274   3.147  0.00165 ** 
# gender1     -0.062708   0.125213  -0.501  0.61650    
# iq_z        -0.002919   0.080241  -0.036  0.97099   
```






















#########################################################################################################
##If requested Compared to MOCK trials
#########################################################################################################
###############################################
## Run and Location effects on GO DECISIONS ##
###############################################
```{r}
# Run effects on the proportion of Go decisions
null.model <- glmer(go ~ (1|SID), data=df, family='binomial')
run.model <- glmer(go ~ run_index + (1|SID), data=df, family='binomial')
anova(null.model, run.model)         #42.751      7  3.727e-07 ***
summary(run.model) #run_index2   0.009882   0.080147   0.123 0.901873    
                   #run_index3  -0.123451   0.080585  -1.532 0.125539    
                   #run_index4  -0.126722   0.080602  -1.572 0.115906    
                   #run_index5   0.060622   0.079843   0.759 0.447689    
                   #run_index6   0.028788   0.079941   0.360 0.718759
                   #run_index7   0.189485   0.079494   2.384 0.017143 *
                   #run_index8   0.276431   0.079348   3.484 0.000494 ***

#From run 1 (alone) go decisions signifcantly increased following both social exlcusion runs

# Condition effects on the proportion of Go decisions
null.model <- glmer(go ~ (1|SID), data=df, family='binomial')
condition.model <- glmer(go ~ condition + (1|SID), data=df, family='binomial')
anova(null.model, condition.model)         #41.358      3  5.491e-09 ***
summary(condition.model) # condition2  -0.13000    0.05703  -2.280   0.0226 *  
                         # condition3   0.03980    0.05653   0.704   0.4814    
                         # condition4   0.22812    0.05620   4.059 4.93e-05 ***

#Go decisions in the mock scanner were siginificantly higher than in the scanner, but significantly lower following social exclusion. Indciating adolescents took fewer risks in the MRI when without a social context, but took signifcantly more risks following social exlucsion in the MRI.

```
#########################################
## Social Context effects on CRASHES ##
#########################################
```{r}
# Run effects on the proportion of Go decisions that resulted in Crashes
null.model <- glmer(go_cr ~ (1|SID), data=df, family='binomial')
run.model <- glmer(go_cr ~ run_index + (1|SID), data=df, family='binomial', control=glmerControl(optimizer="bobyqa"))
anova(null.model, run.model) #12.569      7    0.08334 .
summary(run.model) #run_index2   0.02396    0.09626   0.249   0.8034    
                   #run_index3  -0.07655    0.09756  -0.785   0.4327    
                   #run_index4   0.01398    0.09626   0.145   0.8846    
                   #run_index5   0.04616    0.09583   0.482   0.6300    
                   #run_index6   0.02784    0.09607   0.290   0.7720    
                   #run_index7   0.16942    0.09428   1.797   0.0723 .  
                   #run_index8   0.19480    0.09399   2.073   0.0382 *

#Teens had significantly more crashs (bad go outcomes) in their last run following social exlcusion than in their first run in the mock scanner alone. Crashes were not signficnatly different across other runs in the scanner.

# Condition effects on the proportion of Go decisions that resulted in Crashes
null.model <- glmer(go_cr ~ (1|SID), data=df, family='binomial')
condition.model <- glmer(go_cr ~ condition + (1|SID), data=df, family='binomial')
anova(null.model, condition.model)         #11.534      3   0.009161 **
summary(condition.model) #condition2  -0.04267    0.06846  -0.623   0.5331    
                         #condition3   0.02504    0.06780   0.369   0.7119    
                         #condition4   0.17016    0.06652   2.558   0.0105 *

```
################################################
## Run and Location effects on STOP DECISIONS ##
################################################
```{r}
# Run effects on the proportion of Stop decisions
null.model <- glmer(stop ~ (1|SID), data=df, family='binomial')
run.model <- glmer(stop ~ run_index + (1|SID), data=df, family='binomial')
anova(null.model, run.model)
#            Df   AIC   BIC  logLik deviance Chisq Chi Df Pr(>Chisq)    
# null.model  2 14781 14796 -7388.5    14777                            
# run.model   9 14742 14808 -7362.0    14724 53.14      7  3.478e-09 ***
summary(run.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept)  0.01615    0.08589   0.188 0.850827    
# run_index2   0.28226    0.07876   3.584 0.000339 ***
# run_index3   0.42172    0.07899   5.339 9.36e-08 ***
# run_index4   0.41536    0.07897   5.260 1.44e-07 ***
# run_index5   0.27706    0.07855   3.527 0.000420 ***
# run_index6   0.31138    0.07864   3.960 7.51e-05 ***
# run_index7   0.14715    0.07831   1.879 0.060219 .  
# run_index8   0.07655    0.07823   0.979 0.327823

# Condition effects on the proportion of Stop decisions
null.model <- glmer(stop ~ (1|SID), data=df, family='binomial')
condition.model <- glmer(stop ~ condition + (1|SID), data=df, family='binomial')
anova(null.model, condition.model)
#                 Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
# null.model       2 14781 14796 -7388.5    14777                             
# condition.model  5 14748 14784 -7368.9    14738 39.273      3  1.519e-08 ***
summary(condition.model) 
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept)  0.15579    0.07643   2.038  0.04152 *  
# condition2   0.27869    0.05597   4.979 6.38e-07 ***
# condition3   0.15439    0.05569   2.772  0.00557 ** 
# condition4  -0.02794    0.05547  -0.504  0.61443 
```
###############################################################################
## Run and Location effects on Stop decisions when there was no crossing car ##
###############################################################################
```{r}
# Run effects on the proportion of Bad Stop decisions
null.model <- glmer(stop_nocar ~ (1|SID), data=df, family='binomial')
run.model <- glmer(stop_nocar ~ run_index + (1|SID), data=df, family='binomial')
anova(null.model, run.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)   
# null.model  2 13058 13072 -6526.8    13054                            
# run.model   9 13051 13117 -6516.5    13033 20.595      7   0.004417 **
summary(run.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.14076    0.07068 -16.140  < 2e-16 ***
# run_index2   0.16523    0.08706   1.898 0.057717 .  
# run_index3   0.26448    0.08584   3.081 0.002063 ** 
# run_index4   0.28522    0.08568   3.329 0.000872 ***
# run_index5   0.13978    0.08691   1.608 0.107753    
# run_index6   0.20472    0.08633   2.372 0.017716 *  
# run_index7   0.10289    0.08726   1.179 0.238334    
# run_index8   0.02331    0.08807   0.265 0.791287

# Condition effects on the proportion of Stop decisions
null.model <- glmer(stop_nocar ~ (1|SID), data=df, family='binomial')
condition.model <- glmer(stop_nocar ~ condition + (1|SID), data=df, family='binomial')
anova(null.model, condition.model)
#                 Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)   
# null.model       2 13058 13072 -6526.8    13054                            
# condition.model  5 13048 13085 -6519.1    13038 15.514      3   0.001426 **
summary(condition.model) 
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.05727    0.05458 -19.371  < 2e-16 ***
# condition2   0.19142    0.06014   3.183  0.00146 ** 
# condition3   0.08903    0.06075   1.466  0.14278    
# condition4  -0.01996    0.06149  -0.325  0.74546
```
#########################################################
## FIGURE 2: Run and Location effects on Task Behavior ##
#########################################################
```{r}
# # Part A: Run and Location effects on Go decisions
# plot_go = df %>% group_by(SID, run_index, condition) %>% summarize(mean_go = mean(go), sd_go = sd(go))
#   
# fig_2a <- ggplot(plot_go, aes(x = run_index, y = mean_go)) +
#   geom_boxplot() +
#   facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
#   labs(x='Run number', y='Propotion of Go decisions') +
#   #coord_cartesian(x=c(10.5,17.5)) + 
#   theme(text = element_text(size=18), axis.text.x = element_text(size=14), 
#         axis.text.y = element_text(size=14), strip.text.x = element_text(size=18)) #+
#   #scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10)) + scale_x_continuous(breaks = 11:17) 
# ggsave('fig_2a.png', fig_2a)
# 
# # Part B: Run and Location effects on Crashes
# plot_go_cr = df %>% group_by(SID, run_index, condition) %>% summarize(mean_go_cr = mean(go_cr), sd_go_cr = sd(go_cr))
#   
# fig_2b <- ggplot(plot_go_cr, aes(x = run_index, y = mean_go_cr)) +
#   geom_boxplot() +
#   facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
#   labs(x='Run number', y='Propotion of Go decisions\nthat resulted in Crashes') +
#   #coord_cartesian(x=c(10.5,17.5)) + 
#   theme(text = element_text(size=18), axis.text.x = element_text(size=14), 
#         axis.text.y = element_text(size=14), strip.text.x = element_text(size=18)) #+
#   #scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10)) + scale_x_continuous(breaks = 11:17) 
# ggsave('fig_2b.png', fig_2b)
```
#####################################################################
## FIGURE 2 ALTERNATIVE: Run and Location effects on Task Behavior ##
#####################################################################
```{r}
# Part A: Run and Condition effects on Go decisions
go_by_sid = df %>% group_by(SID, run_index, condition) %>% summarize(mean_go = mean(go))
plot_group_go = go_by_sid %>% group_by(run_index, condition) %>% summarize(mean=mean(mean_go), 
                                                                    sd=sd(mean_go), 
                                                                    n=70, # entered manually (could not be calculated because 127 has 140 trials, whereas all other subjects have 160 trials)
                                                                    se=sd/sqrt(n), 
                                                                    ci=qt(0.975, df=n-1)*se) 
  
fig_2a <- ggplot(plot_group_go, aes(x = run_index, y = mean, group=1)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci)) +
  facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
  labs(x='Run number', y='Propotion of Go decisions') #+
  #coord_cartesian(x=c(10.5,17.5)) + 
  theme(text = element_text(size=18), axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14), strip.text.x = element_text(size=18)) #+
  #scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10)) + scale_x_continuous(breaks = 11:17) 
ggsave('fig_2a.png', fig_2a)

# Part B: Run and Location effects on Crashes
go_cr_by_sid = df %>% group_by(SID, run_index, condition) %>% summarize(mean_go_cr = mean(go_cr))
plot_group_go_cr = go_cr_by_sid %>% group_by(run_index, condition) %>% summarize(mean = mean(mean_go_cr), 
                                                                    sd = sd(mean_go_cr), 
                                                                    n=70, # entered manually (could not be calculated because 127 has 140 trials, whereas all other subjects have 160 trials)
                                                                    se=sd/sqrt(n), 
                                                                    ci=qt(0.975, df=n-1)*se) 

fig_2b <- ggplot(plot_group_go_cr, aes(x = run_index, y = mean, group=1)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci)) +
  facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
  labs(x='Run number', y='Propotion of Go decisions\nthat resulted in Crashes') #+
  #coord_cartesian(x=c(10.5,17.5)) + 
  theme(text = element_text(size=18), axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14), strip.text.x = element_text(size=18)) #+
  #scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10)) + scale_x_continuous(breaks = 11:17) 
ggsave('fig_2b.png', fig_2b)

# Part C: Run and Location effects on Stop decisions
stop_by_sid = df %>% group_by(SID, run_index, condition) %>% summarize(mean_stop = mean(stop))
plot_group_stop = stop_by_sid %>% group_by(run_index, condition) %>% summarize(mean = mean(mean_stop), 
                                                                    sd = sd(mean_stop), 
                                                                    n=70, # entered manually (could not be calculated because 127 has 140 trials, whereas all other subjects have 160 trials)
                                                                    se=sd/sqrt(n), 
                                                                    ci=qt(0.975, df=n-1)*se) 

fig_2c <- ggplot(plot_group_stop, aes(x = run_index, y = mean, group=1)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci)) +
  facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
  labs(x='Run number', y='Propotion of Stop decisions') #+
  #coord_cartesian(x=c(10.5,17.5)) + 
  theme(text = element_text(size=18), axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14), strip.text.x = element_text(size=18)) #+
  #scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10)) + scale_x_continuous(breaks = 11:17) 
ggsave('fig_2c.png', fig_2c)

# Part d: Run and Location effects on Bad Stop decisions
stop_nocar_by_sid = df %>% group_by(SID, run_index, condition) %>% summarize(mean_stop_nocar = mean(stop_nocar))
plot_group_stop_nocar = stop_nocar_by_sid %>% group_by(run_index, condition) %>% summarize(mean = mean(mean_stop_nocar), 
                                                                    sd = sd(mean_stop_nocar), 
                                                                    n=70, # entered manually (could not be calculated because 127 has 140 trials, whereas all other subjects have 160 trials)
                                                                    se=sd/sqrt(n), 
                                                                    ci=qt(0.975, df=n-1)*se) 

fig_2d <- ggplot(plot_group_stop_nocar, aes(x = run_index, y = mean, group=1)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = mean-ci, ymax = mean+ci)) +
  facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
  labs(x='Run number', y='Propotion of Bad Stop decisions') #+
  #coord_cartesian(x=c(10.5,17.5)) + 
  theme(text = element_text(size=18), axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14), strip.text.x = element_text(size=18)) #+
  #scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10)) + scale_x_continuous(breaks = 11:17) 
ggsave('fig_2d.png', fig_2d)
```
##############################################
## Run and Location effects on GO DECISIONS ##
##############################################
```{r}
# Run effects on the proportion of Go decisions
null.model <- glmer(go ~ (1|SID), data=df, family='binomial')
run.model <- glmer(go ~ run_index + (1|SID), data=df, family='binomial')
anova(null.model, run.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
# null.model  2 14484 14499 -7240.1    14480                             
# run.model   9 14456 14521 -7218.7    14438 42.751      7  3.727e-07 ***
summary(run.model)
# Fixed effects:
#              Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.487443   0.089386  -5.453 4.95e-08 ***
# run_index2   0.009882   0.080147   0.123 0.901873    
# run_index3  -0.123451   0.080585  -1.532 0.125539    
# run_index4  -0.126722   0.080602  -1.572 0.115906    
# run_index5   0.060622   0.079843   0.759 0.447689    
# run_index6   0.028788   0.079941   0.360 0.718759    
# run_index7   0.189485   0.079494   2.384 0.017143 *  
# run_index8   0.276431   0.079348   3.484 0.000494 ***

# Location effects on the proportion of Go decisions
null.model <- glmer(go ~ (1|SID), data=df, family='binomial')
location.model <- glmer(go ~ condition + (1|SID), data=df, family='binomial')
anova(null.model, location.model)
#                Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
# null.model      2 14484 14499 -7240.1    14480                             
# location.model  5 14449 14486 -7219.4    14439 41.358      3  5.491e-09 ***
summary(location.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.48250    0.07997  -6.034 1.60e-09 ***
# condition2  -0.13000    0.05703  -2.280   0.0226 *  
# condition3   0.03980    0.05653   0.704   0.4814    
# condition4   0.22812    0.05620   4.059 4.93e-05 ***
```
#########################################
## Run and Location effects on CRASHES ##
#########################################
```{r}
# Run effects on the proportion of Go decisions that resulted in Crashes
null.model <- glmer(go_cr ~ (1|SID), data=df, family='binomial')
run.model <- glmer(go_cr ~ run_index + (1|SID), data=df, family='binomial')
anova(null.model, run.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)  
# null.model  2 11106 11120 -5550.9    11102                           
# run.model   9 11107 11173 -5544.7    11089 12.569      7    0.08334 .
summary(null.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.42480    0.05717  -24.92   <2e-16 ***

# Location effects on the proportion of Go decisions that resulted in Crashes
null.model <- glmer(go_cr ~ (1|SID), data=df, family='binomial')
location.model <- glmer(go_cr ~ condition + (1|SID), data=df, family='binomial')
anova(null.model, location.model)
#                Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)   
# null.model      2 11106 11120 -5550.9    11102                            
# location.model  5 11100 11137 -5545.2    11090 11.534      3   0.009161 **
summary(location.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.46494    0.07098 -20.639   <2e-16 ***
# condition2  -0.04267    0.06846  -0.623   0.5331    
# condition3   0.02504    0.06780   0.369   0.7119    
# condition4   0.17016    0.06652   2.558   0.0105 *
```
################################################################
## Age effects on GO DECISIONS while controlling for Sex & IQ ##
################################################################
```{r}
# Linear Age effects on the proportion of Go decisions (by run_index)
null.model <- glmer(go ~ run_index + gender + iq_z + (1|SID), data=df, family='binomial')
main.model <- glmer(go ~ age_c + run_index + gender + iq_z + (1|SID), data=df, family='binomial')
interaction.model <- glmer(go ~ age_c * run_index + gender + iq_z + (1|SID), data=df, family='binomial')

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model 11 14459 14539 -7218.3    14437                         
# main.model 12 14461 14548 -7218.3    14437 0.0297      1     0.8632
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model        11 14459 14539 -7218.3    14437                         
# interaction.model 19 14463 14602 -7212.5    14425 11.633      8     0.1684
# anova(main.model, interaction.model)

summary(null.model)
# Fixed effects:
#              Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.409811   0.123514  -3.318 0.000907 ***
# run_index2   0.009978   0.080138   0.125 0.900909    
# run_index3  -0.123439   0.080572  -1.532 0.125516    
# run_index4  -0.126733   0.080586  -1.573 0.115802    
# run_index5   0.060613   0.079826   0.759 0.447663    
# run_index6   0.028791   0.079930   0.360 0.718693    
# run_index7   0.189501   0.079477   2.384 0.017110 *  
# run_index8   0.276416   0.079327   3.485 0.000493 ***
# gender1     -0.128073   0.143659  -0.892 0.372659    
# iq_z        -0.019440   0.092818  -0.209 0.834102

# Linear Age effects on the proportion of Go decisions (by location)
null.model <- glmer(go ~ condition + gender + iq_z + (1|SID), data=df, family='binomial')
main.model <- glmer(go ~ age_c + condition + gender + iq_z + (1|SID), data=df, family='binomial')
interaction.model <- glmer(go ~ age_c * condition + gender + iq_z + (1|SID), data=df, family='binomial')

anova(null.model, main.model)
#            Df   AIC   BIC logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model  7 14452 14503  -7219    14438                         
# main.model  8 14454 14513  -7219    14438 0.0297      1     0.8632
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model         7 14452 14503 -7219.0    14438                         
# interaction.model 11 14455 14535 -7216.3    14433 5.4341      4     0.2456
# anova(main.model, interaction.model)

summary(null.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.40485    0.11697  -3.461 0.000538 ***
# condition2  -0.13006    0.05703  -2.281 0.022563 *  
# condition3   0.03975    0.05653   0.703 0.481995    
# condition4   0.22807    0.05620   4.058 4.94e-05 ***
# gender1     -0.12805    0.14371  -0.891 0.372916    
# iq_z        -0.01943    0.09284  -0.209 0.834216
```
###############
## FIGURE 4A ##
###############
```{r}
# Part A: Go decisions plotted against Age
# df$pred_go <- predict(interaction.model, newdata=df, re.form=NA, type='response')
# 
# fig_4a <- ggplot(data=df, aes(x=age, y=pred_go, color=condition)) +
#   geom_line(aes(group=condition), size=1) +
#   #facet_grid(.~tds_group, scales='free', labeller=as_labeller(group_labels)) +
#   labs(x='Age', y='Predicted probability of Go decisions', color='Location') +
#   theme(text = element_text(size=16)) +
#   #coord_cartesian(x=c(-3, 4)) +
#   scale_colour_discrete(labels=condition_labels)
# ggsave('fig_4a.png', fig_4a)

# pGo <- df %>% group_by(SID, condition) %>% summarize(pGo = mean(go))
# pGo_by_age <- merge(pGo, demo, by = 'SID')

# ggplot(pGo_by_age, aes(x = age, y = pGo, color=condition), stat_smooth(method = loess)) +
#   geom_point() +
#   geom_line(aes(group=condition), size=1) +
#   #geom_errorbar(aes(ymax=mean + ci, ymin=mean - ci), width=0.5, position=position_dodge(.2)) +
#   #facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
#   labs(x='Age (mean-centered)', y='Proportion of Go decisions', color='Location')
```
######################################################################
## Age Group effects on GO DECISIONS while controlling for Sex & IQ ##
######################################################################
```{r}
# Age group effects on the proportion of Go decisions (by run_index)
# null.model <- glmer(go ~ run_index + gender + iq_z + (1|SID), data=df, family='binomial')
# main.model <- glmer(go ~ age_group + run_index + gender + iq_z + (1|SID), data=df, family='binomial')
# interaction.model <- glmer(go ~ age_group * run_index + gender + iq_z + (1|SID), data=df, family='binomial', control=glmerControl(optimizer="bobyqa"))
# 
# anova(null.model, main.model)
# anova(null.model, interaction.model)
# anova(main.model, interaction.model)
# 
# summary(null.model)
# 
# # Age group effects on the proportion of Go decisions (by location)
# null.model <- glmer(go ~ condition + gender + iq_z + (1|SID), data=df, family='binomial')
# main.model <- glmer(go ~ age_group + condition + gender + iq_z + (1|SID), data=df, family='binomial')
# interaction.model <- glmer(go ~ age_group * condition + gender + iq_z + (1|SID), data=df, family='binomial')
# 
# anova(null.model, main.model)
# anova(null.model, interaction.model)
# anova(main.model, interaction.model)
# 
# summary(null.model)
```
###########################################################
## Age effects on CRASHES while controlling for Sex & IQ ##
###########################################################
```{r}
# Age effects on the proportion of Go decisions that resulted in Crashes (by run_index)
null.model <- glmer(go_cr ~ run_index + gender + iq_z + (1|SID), data=df, family='binomial')
main.model <- glmer(go_cr ~ age_c + run_index + gender + iq_z + (1|SID), data=df, family='binomial')
interaction.model <- glmer(go_cr ~ age_c * run_index + gender + iq_z + (1|SID), data=df, family='binomial', control=glmerControl(optimizer="bobyqa"))

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model 11 11111 11191 -5544.3    11089                         
# main.model 12 11113 11200 -5544.3    11089 0.0121      1     0.9124
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model        11 11111 11191 -5544.3    11089                         
# interaction.model 19 11114 11253 -5538.0    11076 12.617      8     0.1257
#anova(main.model, interaction.model)

summary(null.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.43537    0.10940 -13.121   <2e-16 ***
# run_index2   0.02410    0.09631   0.250   0.8024    
# run_index3  -0.07655    0.09762  -0.784   0.4329    
# run_index4   0.01396    0.09631   0.145   0.8847    
# run_index5   0.04615    0.09588   0.481   0.6303    
# run_index6   0.02783    0.09612   0.290   0.7721    
# run_index7   0.16941    0.09433   1.796   0.0725 .  
# run_index8   0.19479    0.09404   2.071   0.0383 *  
# gender1     -0.09179    0.11380  -0.807   0.4199    
# iq_z         0.01449    0.07332   0.198   0.8433  

# Age effects on the proportion of Go decisions that resulted in Crashes (by location)
null.model <- glmer(go_cr ~ condition + gender + iq_z + (1|SID), data=df, family='binomial')
main.model <- glmer(go_cr ~ age_c + condition + gender + iq_z + (1|SID), data=df, family='binomial')
interaction.model <- glmer(go_cr ~ age_c * condition + gender + iq_z + (1|SID), data=df, family='binomial')

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model  7 11104 11155 -5544.8    11090                         
# main.model  8 11106 11164 -5544.8    11090 0.0121      1     0.9125
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model         7 11104 11155 -5544.8    11090                         
# interaction.model 11 11109 11190 -5543.7    11087 2.3199      4     0.6772
# anova(main.model, interaction.model)

summary(null.model)
#Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.42335    0.09822 -14.491   <2e-16 ***
# condition2  -0.04274    0.06848  -0.624   0.5325    
# condition3   0.02496    0.06781   0.368   0.7128    
# condition4   0.17009    0.06652   2.557   0.0106 *  
# gender1     -0.09174    0.11381  -0.806   0.4202    
# iq_z         0.01450    0.07332   0.198   0.8433
```
###############
## FIGURE 4B ##
###############
```{r}
# Part B: Crashes
# crashes <- df %>% distinct(SID, gender_flip, condition, run_index, crash.count)
# # new.row = c(127, 'Male', 1, 2, NA)
# # crashes <- rbind(crashes, new.row)
# 
# plot.crashes <- crashes %>% group_by(gender_flip, condition, run_index) %>%
#   summarize(mean = mean(crash.count), sd = sd(crash.count), n = n(), se = sd/sqrt(n), ci=qt(0.975, df=n-1)*se)
# 
# ggplot(plot.crashes, aes(x = run_index, y = mean, color=gender_flip)) +
#   geom_point(position=position_dodge(.1), size=3) +
#   geom_line(aes(group=gender_flip), size=1) +
#   geom_errorbar(aes(ymax=mean + ci, ymin=mean - ci), width=0.5, position=position_dodge(.2)) +
#   facet_grid(.~condition, scales='free', labeller=as_labeller(condition_labels)) +
#   labs(x='Run number', y='Crashes', color='Sex') +
#   scale_y_continuous(breaks = c(3, 4, 5))
```
#################################################################
## Age Group effects on CRASHES while controlling for Sex & IQ ##
#################################################################
```{r}
# # Age group effects on the proportion of Go decisions that resulted in Crashes (by run_index)
# null.model <- glmer(go_cr ~ run_index + gender + iq_z + (1|SID), data=df, family='binomial')
# main.model <- glmer(go_cr ~ age_group + run_index + gender + iq_z + (1|SID), data=df, family='binomial')
# interaction.model <- glmer(go_cr ~ age_group * run_index + gender + iq_z + (1|SID), data=df, family='binomial', control=glmerControl(optimizer="bobyqa"))
# 
# anova(null.model, main.model)
# anova(null.model, interaction.model)
# anova(main.model, interaction.model)
# 
# summary(null.model)
# 
# # Age group effects on the proportion of Go decisions that resulted in Crashes (by location)
# null.model <- glmer(go_cr ~ condition + gender + iq_z + (1|SID), data=df, family='binomial')
# main.model <- glmer(go_cr ~ age_group + condition + gender + iq_z + (1|SID), data=df, family='binomial')
# interaction.model <- glmer(go_cr ~ age_group * condition + gender + iq_z + (1|SID), data=df, family='binomial')
# 
# anova(null.model, main.model)
# anova(null.model, interaction.model)
# anova(main.model, interaction.model)
# 
# summary(null.model)
```
####################################################################
## Puberty effects on GO DECISIONS while controlling for Sex & IQ ##
####################################################################
```{r}
# Puberty effects on the proportion of Go decisions (by run_index)
null.model <- glmer(go ~ run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial')
main.model <- glmer(go ~ PDS_mean_score + run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))
interaction.model <- glmer(go ~ PDS_mean_score * run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model 11 14015 14095 -6996.4    13993                         
# main.model 12 14016 14104 -6996.2    13992 0.5076      1     0.4762
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance Chisq Chi Df Pr(>Chisq)
# null.model        11 14015 14095 -6996.4    13993                        
# interaction.model 19 14024 14162 -6992.8    13986 7.241      8     0.5109
# anova(main.model, interaction.model)

summary(null.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.42813    0.12512  -3.422 0.000622 ***
# run_index2  -0.01289    0.08140  -0.158 0.874145    
# run_index3  -0.14070    0.08183  -1.719 0.085561 .  
# run_index4  -0.15776    0.08193  -1.926 0.054159 .  
# run_index5   0.03946    0.08105   0.487 0.626312    
# run_index6   0.01318    0.08115   0.162 0.870942    
# run_index7   0.17243    0.08066   2.138 0.032553 *  
# run_index8   0.25559    0.08050   3.175 0.001499 ** 
# gender      -0.08017    0.14560  -0.551 0.581886    
# iq_z        -0.03955    0.09357  -0.423 0.672498 

# Puberty effects on the proportion of Go decisions (by location)
null.model <- glmer(go ~ condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
main.model <- glmer(go ~ PDS_mean_score + condition + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))
interaction.model <- glmer(go ~ PDS_mean_score * condition + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model  7 14008 14059 -6997.0    13994                         
# main.model  8 14010 14068 -6996.8    13994 0.5077      1     0.4761
anova(null.model, interaction.model)
#                   Df   AIC   BIC logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model         7 14008 14059  -6997    13994                         
# interaction.model 11 14012 14092  -6995    13990 4.0912      4     0.3938
# anova(main.model, interaction.model)

summary(null.model)
# Fixed effects:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -0.43451    0.11840  -3.670 0.000243 ***
# condition2  -0.14281    0.05797  -2.464 0.013755 *  
# condition3   0.03276    0.05742   0.571 0.568336    
# condition4   0.22051    0.05706   3.865 0.000111 ***
# gender      -0.08019    0.14554  -0.551 0.581652    
# iq_z        -0.03956    0.09355  -0.423 0.672400 
```
###############################################################
## Puberty effects on CRASHES while controlling for Sex & IQ ##
###############################################################
```{r}
# Puberty effects on the proportion of Go decisions that resulted in Crashes (by run_index)
null.model <- glmer(go_cr ~ run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))
main.model <- glmer(go_cr ~ PDS_mean_score + run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))
interaction.model <- glmer(go_cr ~ PDS_mean_score * run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model 11 10718 10798 -5348.1    10696                         
# main.model 12 10720 10807 -5347.9    10696 0.2916      1     0.5892
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model        11 10718 10798 -5348.1    10696                         
# interaction.model 19 10728 10867 -5345.1    10690 5.9499      8     0.6528
# anova(main.model, interaction.model)

summary(null.model)
# Fixed effects:
#               Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.452e+00  1.112e-01 -13.052   <2e-16 ***
# run_index2   1.047e-02  9.803e-02   0.107   0.9149    
# run_index3  -8.419e-02  9.928e-02  -0.848   0.3964    
# run_index4   1.550e-06  9.804e-02   0.000   1.0000    
# run_index5   2.399e-02  9.769e-02   0.246   0.8061    
# run_index6   1.443e-02  9.784e-02   0.148   0.8827    
# run_index7   1.571e-01  9.597e-02   1.636   0.1017    
# run_index8   1.878e-01  9.560e-02   1.964   0.0495 *  
# gender      -5.697e-02  1.158e-01  -0.492   0.6228    
# iq_z         1.579e-03  7.421e-02   0.021   0.9830 

# Puberty effects on the proportion of Go decisions that resulted in Crashes (by location)
null.model <- glmer(go_cr ~ condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
main.model <- glmer(go_cr ~ PDS_mean_score + condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
interaction.model <- glmer(go_cr ~ PDS_mean_score * condition + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))

anova(null.model, main.model)
#            Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model  7 10711 10762 -5348.5    10697                         
# main.model  8 10713 10771 -5348.4    10697 0.2916      1     0.5892
anova(null.model, interaction.model)
#                   Df   AIC   BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
# null.model         7 10711 10762 -5348.5    10697                         
# interaction.model 11 10718 10798 -5347.9    10696 1.2272      4     0.8736
# anova(main.model, interaction.model)

summary(null.model) 
# Fixed effects:
#              Estimate Std. Error z value Pr(>|z|)    
# (Intercept) -1.446446   0.099948 -14.472   <2e-16 ***
# condition2  -0.046798   0.069761  -0.671   0.5023    
# condition3   0.013987   0.069143   0.202   0.8397    
# condition4   0.167249   0.067742   2.469   0.0136 *  
# gender      -0.056937   0.115860  -0.491   0.6231    
# iq_z         0.001585   0.074214   0.021   0.9830
```
######################################################################
## PDS Group effects on GO DECISIONS while controlling for Sex & IQ ##
######################################################################
```{r}
# # PDS group effects on the proportion of Go decisions (by run_index)
# null.model <- glmer(go ~ run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial')
# main.model <- glmer(go ~ pds_group + run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial')
# interaction.model <- glmer(go ~ pds_group * run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))
# 
# anova(null.model, main.model)
# anova(null.model, interaction.model)
# anova(main.model, interaction.model)
# 
# summary(null.model)
# 
# # Age group effects on the proportion of Go decisions (by location)
# null.model <- glmer(go ~ condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
# main.model <- glmer(go ~ pds_group + condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
# interaction.model <- glmer(go ~ pds_group * condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
# 
# anova(null.model, main.model)
# anova(null.model, interaction.model)
# anova(main.model, interaction.model)
# 
# summary(null.model)
```
#################################################################
## PDS Group effects on CRASHES while controlling for Sex & IQ ##
#################################################################
```{r}
# PDS group effects on the proportion of Go decisions that resulted in Crashes (by run_index)
# null.model <- glmer(go_cr ~ run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial')
# main.model <- glmer(go_cr ~ pds_group + run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial')
# interaction.model <- glmer(go_cr ~ pds_group * run_index + gender + iq_z + (1|SID), data=df_pds, family='binomial', control=glmerControl(optimizer="bobyqa"))
# 
# anova(null.model, main.model)
# anova(null.model, interaction.model)
# anova(main.model, interaction.model)
# 
# summary(null.model)
# 
# # PDS group effects on the proportion of Go decisions that resulted in Crashes (by location)
# null.model <- glmer(go_cr ~ condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
# main.model <- glmer(go_cr ~ pds_group + condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
# interaction.model <- glmer(go_cr ~ pds_group * condition + gender + iq_z + (1|SID), data=df_pds, family='binomial')
# 
# anova(null.model, main.model)
# anova(null.model, interaction.model)
# anova(main.model, interaction.model)
# 
# summary(null.model)
```