---
title: "CTQ-to-ACES"
author: "Theresa Cheng"
date: "February 28, 2018"
output: html_document
---

```{r setup, include=FALSE}

#Check if the packages we need are installed, and if not, install them
packages = c("dplyr", "tidyr", "ggplot2")

# load packages, install as needed
package.check <- lapply(packages, FUN = function(x) {
  if (!require(x, character.only = TRUE)) {
    install.packages(x, dependencies = TRUE)
    library(x, character.only = TRUE) }})

setwd("/projects/dsnlab/tds/TDS_scripts/rsfMRI/cheng_fnl/ctq-to-aces")

# load subscale/scored data
df_raw <- read.csv("SP_subjects_ACE_CTQ.csv", header=TRUE)
sapply(df_raw, class)

# subset data to participants WITH CTQ: for rows that start w/ CTQ, calculate row sum
# if the row sum is NOT NA, then subset it from the dataframe
df_wCTQ <- df_raw[!is.na(rowSums(select(df_raw, starts_with("CTQ")))),]
```

## Need to determine mappings between ACE and CTQ questionnaires, write those out here

## Need to take into account minimization scores (any score higher than 0 implies potential underreporting/false negatives)

## Write functions for creating each type of descriptive, then a master function to call them all on the data

```{r descriptives function, include=FALSE}

# This function describes your sample. 
# It takes the following inputs:
# df: dataframe w/ header; leftmost column is subject IDs (SID), other columns represent a variable that you would like described.
# Note that variables will be summarized if they are numeric, integers, or factors. Strings will be ignored. 

sampleDescriptives <- function(df){

  # return the total number of subjects and list of all variables
  df_gen= df %>% 
    filter(is.na==FALSE) %>% # remove empty rows
    nrow(df) # count the number of rows
  
  return(kable(df_gen, caption="General"))
  
  # return missing data per variable
  #df_mi = df %>% 
  #  apply(2, summarise(colnames(.)= sum(.,na.rm=TRUE)) 

  #return(kable(df_mi, caption="Missing data"))
  ## return a boxplot comparing all variables. will not look great w/ vastly different scales
  #
  #
  ## return a histogram or scatterplot per variable
  #apply

}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
